### 2012-07-25 docs/initial_model.tex
Latex file for initial model

\documentclass[11pt,BCOR2mm,DIV14]{scrartcl}
\usepackage[Glenn]{fncychap}
%For symbols in T1 encoding.
\usepackage{textcomp}
\usepackage[colorinlistoftodos, textwidth=4cm, shadow, textsize=tiny]{todonotes}
\usepackage{amsmath,amsfonts,graphicx,ncsg3,comment,typearea,pifont}
\usepackage{xcomment,color, psfrag,enumerate,scrpage2,xspace,listings,wasysym, 
comment}
\usepackage{termcal}

%For fancy tables
\usepackage{booktabs}

%For symbols in T1 encoding.
\usepackage{textcomp}
\begin{document}

\section*{Thoughts}

To get things rolling, I thought we could use the model below - if we can't make progress with this model, then more complicated processes aren't really an option! This is only a thought, I'm happy for other suggestions.

At the end, I've given a couple of associated inference problems. In particular, the likelihoods in figure \ref{F2} are \textit{banana shaped}, and so exploring the space could be tricky.

\section*{Immigration death model with counts}

This model has two species, $N(t)$ and $C(t)$. The first reaction represents a constant immigration rate, and occurs with rate $\alpha$. The second reaction represents death in the $N$ population and occurs with rate $\mu N(t)$. The model can be represented by the coupled (pseudo) reactions, 
\begin{equation}\label{1}
R_1: \emptyset  \xrightarrow{\phantom{a}\alpha\phantom{a}} N 
\quad \text{and} \quad
R_2: N  \xrightarrow{\phantom{a}\mu\phantom{a}} C .
\end{equation}
Essentially, species $C(t)$ is the number of deaths that has occurred up until time $t$. Hence, species $C$ is a monotonically increasing\footnote{This model is used in physics, where photons of light are fired into a box and we only observe photons leaving the box.}. The forward Kolmogorov equation (or CME) for this model is
\[
dp_{nc}(t)/dt = \alpha p_{n-1, c}(t) +  \mu (n+1) p_{n+1,c-1}(t) 
- (\alpha + \mu n) p_{nc}(t) \;.
\]
This equation can be solved exactly using a generating function approach.

\subsection*{Moments}

The general idea of \textit{moment closure} is to represent the analytically intractable moments of the process as a set of ODEs. The solutions of these ODEs provide approximations for the moments. With this particular system, we can solve the ODEs analytically - so the moments are exact.

The marginal means of the process are:
\begin{align*}
E[n(t) | n(0) = n_0 ] &= \frac{\alpha}{\mu}(1-e^{-\mu t}) + n_0 e^{-\mu t} \\
E[c(t) | n(0) = n_0, c_0=0] &= \frac{\alpha}{\mu} (\mu t + e^{-\mu t} - 1) + \alpha n_0(1-e^{-\mu t}) \;.
\end{align*}
Notice that as $t \rightarrow \infty$,
\begin{align*}
E[n(t) | n(0) = n_0 ] &= \frac{\alpha}{\mu}\\
E[c(t) | n(0) = n_0, c_0=0] &\simeq \alpha t + n_0 \;.
\end{align*}
The marginal variances are a bit more messy, but still fairly tractable:
\begin{align*}
Var[n(t) | n_0]  &= \left(\frac{\alpha}{\mu} + n_0e^{-\mu t}\right)(1-e^{-\mu t})\\
Var[c(t) | n_0, c_0=0]  &= \frac{\alpha}{\mu}(e^{-\mu t} - 1) + \alpha t + n_0 \mu e^{-\mu t} - \frac{n_0 e^{-2\mu t}}{\mu} \;. 
\end{align*}
The covariance for $N$ and $C$ is
\begin{align*}
E[n(t), c(t)| n_0, c_0=0] &= \frac{\alpha^2}{\mu^2}(-1+e^{-\mu t}+\mu t)(1-e^{-\mu t}) + 
\frac{\alpha}{\mu} (-1+e^{-\mu t}+\mu t) n_0 e^{-\mu t} + \\
&\quad +\frac{\alpha}{\mu} (1-e^{-\mu t})^2 n_0 + 
n_0^2  (1-e^{-\mu t})e^{-\mu t}
- n_0(1-e^{-\mu t})e^{-\mu t}\;.
\end{align*}

\section*{Inference}

Two possible scenarios that I've looked at in the past are:
\begin{enumerate}
\item We observe species $N$ at discrete time points $t_0, t_1, \ldots, t_{n+1}$. Assuming no error in the observations and a uniform prior, we obtain the likelihood (or posterior) surfaces shown in figure \ref{F1}.
\item We observe all deaths in the process, i.e. we observe species $C$ exactly. Here we get likelihood/posterior surfaces of the type in \ref{F2}
\end{enumerate}
In both cases, there is no observation error involved. Ironically, this actually makes inference very tricky in an ABC/MCMC. Since we need our simulations to exactly hit the target.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{graphs/likelihood_disc_2}
\caption{Plots to show the exact discrete time point likelihood, for $\alpha =400$, $\mu=20$ and $n_0=0$.}\label{F1}
\end{figure}
\clearpage
\newpage
\begin{figure}[t]
\centering
\includegraphics[width=0.8\textwidth]{graphs/n0_0-crop}
\includegraphics[width=0.8\textwidth]{graphs/n0_20-crop}
\includegraphics[width=0.8\textwidth]{graphs/n0_40-crop}
\caption{Likelihood surface plot using the 100 death times from a single realisation, when the initial population is known (red) and unknown (black). Parameters were $\alpha = 0.05$, $\mu=0.05$ and (a) $n_0=0$, (b) $n_0 = 20$, (c) $n_0 = 40$. The true parameters are shown as a blue dot.
Note: the $y$-axis label should be $\mu$ not $\eta$.}\label{F2}
\end{figure}

% 
% Following \citet{Matis06}, we assume a linear aphid population birth rate of $\lambda N(t)$ where 
% $N(t)$ denotes the size of the aphid population at time $t$. As discussed in \citet{Prajneshu98}, aphids 
% excrete honey-dew, forming a cover on the leaf surface and causing aphid starvation. As the area covered by excretion 
% at time $t$ is proportional to the cumulative population size at time $t$, $C(t)$, we assume a death rate 
% of $\mu N(t)C(t)$ and for simplicity, assume that there is no removal or decomposition of honey-dew 
% \citep{Matis06,Matis07a,Matis08}. The model can be represented by the coupled (pseudo) reactions, 
% \begin{align}
% N & \xrightarrow{\phantom{a}\lambda\phantom{a}} 2N + C \label{2.1} \\
% N+C & \xrightarrow{\phantom{a}\mu\phantom{a}} C \label{2.2}
% \end{align}
% since clearly, an occurrence of (\ref{2.1}) will lead to a unit increase in both $N$ and $C$ whereas the reaction in  (\ref{2.2}) will give a unit decrease in $N$ but leave $C$ unchanged. Such models are known in the literature as stochastic kinetic models; see \citet{Wilkinson06} for a concise introduction. We can express the probabilistic laws governing the time evolution of the process by considering a small interval $(t,t+dt]$, namely
% \begin{align}
% \Pr\left\{N(t+dt)=n(t)+1,\,C(t+dt)=c(t)+1\,|\,n(t),c(t)\right\}&=\lambda n(t)dt+o(dt) \label{2.3} \\
% \Pr\left\{N(t+dt)=n(t)-1,\,C(t+dt)=c(t)\,|\,n(t),c(t)\right\}&=\mu n(t)c(t)dt+o(dt),\label{2.4}
% \end{align}
% and we adopt the convention that upper case denotes random variable and lower case denotes the realisation. 
% The expressions in (\ref{2.3}) and (\ref{2.4}) describe a Markov jump process where each event occurs at a particular rate dependent on the current state of the system. Note that ignoring stochasticity leads to a deterministic model where the time course behaviour of 
% $N(t)$ and $C(t)$ is described by the set of differential equations,
% \[
% \left\{\begin{array}{l}
% \displaystyle\frac{dN(t)}{dt}=\lambda N(t)-\mu N(t)C(t)\\
% \\
% \displaystyle\frac{dC(t)}{dt}= \lambda N(t)
% \end{array}\right.
% \] 
% 
% 
% 
% 
% 
% 
% Suppose we have two species $X$ and $C$. 
% \[
% R_1: \emptyset \xrightarrow{\alpha} X 
% \quad \text{and} \quad 
% R_2: X + C \xrightarrow{\mu X C} 2C
% \]
%

\end{document}

### 2012-07-27 Simulation/simulation.R
Adding some R code to simulation the immigration-death count model

@@ -1,0 +1,63 @@
+##Discretise a fully observed stochastic simulation
+discretise = function(dd, tstep) {
+    time = tstep
+    dd_dis = dd[1:(max(dd$time)/tstep+1),]
+    j = 2
+    for(i in 1:(nrow(dd)-1)) {
+        while(dd$time[i] < time && dd$time[i+1] > time) {
+            dd_dis[j,] = c(time, dd[i, 2:ncol(dd)])
+            time = time + tstep
+            j = j + 1
+        }
+    }
+    return(dd_dis)
+}
+
+gillespie = function(IC, pars, maxtime=10) {
+    time = 0; tstep=0; i=1 
+    X1 = IC[1]; X2 = IC[2]
+    
+    i = 1
+    pop1 = numeric(1000); pop2 = numeric(1000); times = numeric(1000)
+    while(time < maxtime) {
+        
+        #Update state vectors
+        pop1[i] = X1; pop2[i] = X2; times[i] = time
+        i = i + 1
+        #Calculate the overall rate
+        total_rate = pars[1] + pars[2]*X1
+        time = time + rexp(1, total_rate)
+
+        #Don't go by maxtime
+        if(time >= maxtime)
+            break;
+        
+        #Choose which reaction happens
+        u = runif(1)
+        if(u<pars[1]/total_rate) {
+            X1 = X1 + 1
+        }else {
+            X1 = X1 - 1
+            X2 = X2 + 1
+        }
+    }
+    #Update state vectors
+    pop1[i] = X1; pop2[i] = X2; times[i] = time
+    dd = data.frame(times, n=pop1, c=pop2)
+    return(dd[1:i,])
+}
+
+set.seed(1)
+dd = gillespie(c(0, 0), c(1, 0.1), 50)
+dd_dis = discretise(dd, 5)
+
+##Plot the data
+par(mfrow=c(1,2))
+plot(dd$times, dd$n, type='s')
+points(dd_dis$times, dd_dis$n, col=2)    
+    
+plot(dd$times, dd$c, type='b')
+points(dd_dis$times, dd_dis$c, col=2)
+
+##Output data as a csv file
+write.table(dd, file="sim.csv", sep=",",row.names=FALSE, col.names=FALSE)

### 2012-07-30 Immigration-death/tensor_calculation.R
Initial tensor calculations

@@ -1,0 +1,48 @@
+##Moments
+##k1 = birth, k2 =death
+E = function(k1, k2, n0, t) {
+    (k1-k1*exp(-k2*t)+n0*exp(-k2*t)*k2)/k2
+}
+
+V = function(k1, k2, n0, t) {
+    (-n0*exp(-2*k2*t)*k2+k1-k1*exp(-k2*t)+n0*exp(-k2*t)*k2)/k2
+}
+
+##First-order 
+dE_dk1 = function(k1, k2,n0, t) {
+    (1-exp(-k2*t))/k2    
+}
+
+dE_dk2 = function(k1, k2,n0, t) {
+    -k1*(1-exp(-k2*t))/k2^2+k1*t*exp(-k2*t)/k2-n0*t*exp(-k2*t)   
+}
+
+##Second-order
+##Derivative of 1/Variance wrt to theta
+d1V_dk1 = function(k1, k2,n0, t) {
+    -mu*(1-exp(-mu*t))/(-n0*exp(-2*mu*t)*mu+alpha-alpha*exp(-mu*t)+n0*exp(-mu*t)*mu)^2
+}
+d1V_dk1 = function(k1, k2,n0, t) {
+    -mu*(2*n0*t*exp(-2*mu*t)*mu-n0*exp(-2*mu*t)+alpha*t*exp(-mu*t)-n0*t*exp(-mu*t)*mu+n0*exp(-mu*t))/(-n0*exp(-2*mu*t)*mu+alpha-alpha*exp(-mu*t)+n0*exp(-mu*t)*mu)^2+1/(-n0*exp(-2*mu*t)*mu+alpha-alpha*exp(-mu*t)+n0*exp(-mu*t)*mu)
+}
+
+Firstorder = function(k1, k2, t, x) {
+    value = 0
+    for(i in 1:(length(x)-1)) {
+        m = E(k1, k2, n0, tau)
+        tau = t[i+1] - t[i]
+        n0 = x[i]
+        
+        ##For k1
+        value = value + dE_dk1(k1,k2,n0,tau)*1/V(k1,k2,n0,tau)*(m-x[i+1])
+        value = value + (m-x[i+1])+d1V_dk1 *(m-x[i+1])
+        
+        ##For k2
+        value = value + dE_dk2(k1,k2,n0,tau)*1/V(k1,k2,n0,tau)*(m-x[i+1])
+        value = value + (m-x[i+1])+d1V_dk2 *(m-x[i+1])
[…]

### 2012-07-30 Simulation/simulation.R
Added headers to csv files

@@ -60,4 +60,4 @@ plot(dd$times, dd$c, type='b')
 points(dd_dis$times, dd_dis$c, col=2)
 
 ##Output data as a csv file
-write.table(dd, file="sim.csv", sep=",",row.names=FALSE, col.names=FALSE)
+write.table(dd_dis, file="sim.csv", sep=",",row.names=FALSE, col.names=FALSE)

### 2012-07-30 Immigration-death/tensor_calculation.R
Added derivatives of the variance wrt theta

@@ -1,5 +1,5 @@
 ##Moments
-##k1 = birth, k2 =death
+##k1 = immigration rate, k2 =death
 E = function(k1, k2, n0, t) {
     (k1-k1*exp(-k2*t)+n0*exp(-k2*t)*k2)/k2
 }
@@ -17,32 +17,35 @@ dE_dk2 = function(k1, k2,n0, t) {
     -k1*(1-exp(-k2*t))/k2^2+k1*t*exp(-k2*t)/k2-n0*t*exp(-k2*t)   
 }
 
-##Second-order
-##Derivative of 1/Variance wrt to theta
-d1V_dk1 = function(k1, k2,n0, t) {
-    -mu*(1-exp(-mu*t))/(-n0*exp(-2*mu*t)*mu+alpha-alpha*exp(-mu*t)+n0*exp(-mu*t)*mu)^2
+##Derivative of Variance wrt to theta
+dV_dk1 = function(k1, k2,n0, t) {
+    (1-exp(-mu*t))/mu
 }
-d1V_dk1 = function(k1, k2,n0, t) {
-    -mu*(2*n0*t*exp(-2*mu*t)*mu-n0*exp(-2*mu*t)+alpha*t*exp(-mu*t)-n0*t*exp(-mu*t)*mu+n0*exp(-mu*t))/(-n0*exp(-2*mu*t)*mu+alpha-alpha*exp(-mu*t)+n0*exp(-mu*t)*mu)^2+1/(-n0*exp(-2*mu*t)*mu+alpha-alpha*exp(-mu*t)+n0*exp(-mu*t)*mu)
+dV_dk2 = function(k1, k2,n0, t) {
+    (2*n0*t*exp(-2*mu*t)*mu-n0*exp(-2*mu*t)+alpha*t*exp(-mu*t)-n0*t*exp(-mu*t)*mu+n0*exp(-mu*t))/mu-(-n0*exp(-2*mu*t)*mu+alpha-alpha*exp(-mu*t)+n0*exp(-mu*t)*mu)/mu^2
 }
 
 Firstorder = function(k1, k2, t, x) {
     value = 0
+    x = dd$n
+    t = dd$times
+    i=1;k1=1;k2=0.1
     for(i in 1:(length(x)-1)) {
-        m = E(k1, k2, n0, tau)
         tau = t[i+1] - t[i]
         n0 = x[i]
         
+        m = E(k1, k2, n0, tau)
         ##For k1
[…]

### 2012-07-30 Simulation/simulation.R

@@ -60,4 +60,4 @@ plot(dd$times, dd$c, type='b')
 points(dd_dis$times, dd_dis$c, col=2)
 
 ##Output data as a csv file
-write.table(dd_dis, file="sim.csv", sep=",",row.names=FALSE, col.names=FALSE)
+write.csv(dd_dis, file="data/immigration_death.csv", row.names=FALSE)

### 2012-07-30 Immigration-death/mcmc.R
MCMC script for immigration-death (no noise)

@@ -1,0 +1,14 @@
+##Prob(x=n(t)|n0=n(0)) for immigration death model
+pn = function (k1, k2, t, n0, x) {
+  k3 = k1/k2*(1-exp(-k2*t))
+  value = 0
+  for(i in 0:x) {
+      value = value + choose(n0, i)*
+          exp(-k2*t*i)*
+          (1-exp(-k2*t))^(n0-i)*
+          dpois(x-i, k3)
+  }
+  return(value)
+}
+
+

### 2012-07-30 Immigration-death/tensor_calculation.R
Metric tensor calculations for ID model

@@ -19,33 +19,163 @@ dE_dk2 = function(k1, k2,n0, t) {
 
 ##Derivative of Variance wrt to theta
 dV_dk1 = function(k1, k2,n0, t) {
-    (1-exp(-mu*t))/mu
+    (1-exp(-k2*t))/k2
 }
 dV_dk2 = function(k1, k2,n0, t) {
-    (2*n0*t*exp(-2*mu*t)*mu-n0*exp(-2*mu*t)+alpha*t*exp(-mu*t)-n0*t*exp(-mu*t)*mu+n0*exp(-mu*t))/mu-(-n0*exp(-2*mu*t)*mu+alpha-alpha*exp(-mu*t)+n0*exp(-mu*t)*mu)/mu^2
+    (2*n0*t*exp(-2*k2*t)*k2-n0*exp(-2*k2*t)+k1*t*exp(-k2*t)-n0*t*exp(-k2*t)*k2+n0*exp(-k2*t))/k2-(-n0*exp(-2*k2*t)*k2+k1-k1*exp(-k2*t)+n0*exp(-k2*t)*k2)/k2^2
 }
 
-Firstorder = function(k1, k2, t, x) {
+##Derivative of 1/Variance wrt to theta
+d1V_dk1 = function(k1, k2, n0, t){
+    v = V(k1,k2,n0,tau)
+    -1/v*dV_dk1(k1,k2,n0,tau)/v
+}
+
+d1V_dk2 = function(k1, k2, n0, t){
+    v = V(k1, k2, n0, tau)
+    -1/v*dV_dk2(k1,k2,n0,tau)/v
+}
+
+##Work out Ll
+L = function(k1, k2, t, x) {
+    n0 = x[1:10]
+    n1 = x[2:11] 
+    means = E(k1, k2, n0, 5)
+    vars = V(k1,k2,n0, 5)
+    
+    value = 0 ;i =1
+    for(i in 1:(length(x)-1)) {
+        tau = t[i+1] - t[i]
+        value = value + log(dnorm(x[i+1], means[i], sqrt(vars[i])))
+    }
+    return(value)
+}
+
+##First-order derivative
+L_deriv_k1 = function(k1, k2, t, x) {
     value = 0
-    x = dd$n
-    t = dd$times
-    i=1;k1=1;k2=0.1
     for(i in 1:(length(x)-1)) {
         tau = t[i+1] - t[i]
         n0 = x[i]
         
[…]

### 2012-07-30 Immigration-death/mcmc.R
Exact likelihood for ID

@@ -11,4 +11,46 @@ pn = function (k1, k2, t, n0, x) {
   return(value)
 }
 
+log_likelihood = function(k1, k2, t, x) {
+    ll = 0
+    #k1 = theta[1];k2 = theta[2]
+    for(i in 1:(length(x)-1)) {
+        tau = t[i+1] - t[i]
+        n0 = x[i]
+        ll = ll + log(pn(k1, k2, tau, n0, x[i+1]))
+    }
+    return(ll)
+}
 
+dd = read.csv("data/immigration_death.csv")
+log_likelihood(k1, k2, dd[,1], dd[,2])
+
+k1 = seq(0,3, 0.005)
+k2 = seq(0,0.4, 0.005)
+d = outer(k1, k2, function(k1, k2) log_likelihood(k1, k2, dd[,1], dd[,2]))
+
+image(k1, k2, exp(d))
+# 
+# prop_theta = function(theta_cur){
+#     theta_cur
+# }
+# 
+# 
+# 
+# 
+# 
+# theta_cur = c(0.1, 0.1)
+# ll_cur = -Inf
+# for(i in 1:iters) {
+#     theta_prop  = prop_theta(theta_cur)
+#     ll_prop = log_likelihood(theta_prop)
+#     
+#     
+#     
+#     
+#     
+#     
+#     
+# }
+# 
+# 

### 2012-07-31 paper/example/biomsample.tex
Paper style file

% biomsample.tex
%
% v1.0 released 12th December 2006 (Dr. S. Sharma, Prof. N. Saxena, and Dr. S. Tahir)
%
% The biomsample.tex file has been amended to highlight
% the proper use of LaTeX2e code with the class file
% and using natbib cross-referencing.
%
\documentclass[useAMS,usenatbib]{biom}
%\documentclass[useAMS,usenatbib,referee]{biom}
%
%
%  Papers submitted to Biometrics should ALWAYS be prepared
%  using the referee option!!!!
%
%
% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib package for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%

\def\bSig\mathbf{\Sigma}
\newcommand{\VS}{V\&S}
\newcommand{\tr}{\mbox{tr}}

%  If you have a landscape table you need to use the rotating package

\usepackage[figuresright]{rotating}

%% \raggedbottom % To avoid glue in typesetteing, sbs>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setcounter{footnote}{2}

\title[This is an Example of Recto Running Head]{This is an Example of
an Article Title This is an Example of an Article Title}

\author{S. Sharma$^{*}$\email{email@address.com} \\
	   Institute of Physics, CA 560034, USA
	   \and 
	   A. Other$^{*}$\email{email1aa@address.com}\\
	   Building, Institute, Street Address, City,
	   Code, Country
	   }

\begin{document}

\date{{\it Received October} 2004. {\it Revised February} 2005.\newline 
{\it Accepted March} 2005.}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2006}

\volume{59}
\artmonth{December}
\doi{10.1111/j.1541-0420.2005.00454.x}

%  This label and the label ``lastpage'' are used by the \pagerange
%  command above to give the page range for the article

\label{firstpage}

%  pub the summary here

\begin{abstract}
The world will little note, nor long remember, what we say here, but
can never forget what they did here. It is for us, the living, rather
to be dedicated here to the unfinished work which they have, thus far,
so nobly carried out. It is rather for us to be here dedicated to the
great task remaining before us--that from these honored dead we take
increased devotion to that cause for which they here gave the last
full measures of devotion--that we here highly resolve that these dead
shall not have died in vain; that this nation shall have a new birth
of freedom; and that this government of the people, by the people, for
the people, shall not perish from the earth. The world will little
note.
\end{abstract}

%
%  Please place your key words in alphabetical order, separated
%  by semicolons, with the first letter of the first word capitalized,
%  and a period at the end of the list.
%

\begin{keywords}
Colostrum; Milk; Milk oligosaccharide; Non-human mammal.
\end{keywords}

\maketitle

\section{Introduction}
\label{s:intro}

It has been well established that RV Tauri variables pobiomss infrared
emission far in excess of their expected blackbody continuum, arising
from their extended cool dust envelopes \citep{b7,b5,b6}. Recently,
\citep{b9} have given detailed descriptions of the near-infrared
properties of RV Tauri stars. In this paper we present an analysis of
the {\it NIFT\/} data of RV Tauri stars with the help of the
far-infrared two-color diagram and a grid computed using a simple
model of the dust envelope. Such two-color plots have already been
employed extensively by several investigators to study the
circumstellar envelopes around milk oligosaccharide and colostrum
objects which are in the late stages of stellar evolution
\citep{b10,b25,b24,b23}.

Table~\ref{t:tableone} summarizes the basic data on the 17 objects
detected at \hbox{60\,$\umu$m}. Apart from the {\it NIFT\/}
identification and the flux densities at 12-, 25-, 60- and 100-$\umu$m
wavebands, it gives the spectroscopic groups of \citet{b20}, the
light-curve clabioms of \citet{b13} and the periods of light
variation. The list, which contains about 20 per cent of all the known
RV Tauri stars, is ebiomntially the same as that given by \citet{b12}.
\begin{table*}
 \centering
 \def\~{\hphantom{0}}
 \begin{minipage}{175mm}
  \caption{It is for us, the living, rather to be
dedicated here to the unfinished work which, so nobly
carried out}
\label{t:tableone}
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{}}
  \Hline
 & & \multicolumn{4}{c}{{Flux density (Jy)} \footnote{Observed by {\em NIFT}.}}\\ [1pt]
\cline{3-7} \\ [-6pt]
{Name}        &  & & & & & {Sp.} & \multicolumn{1}{r}{Period}& \multicolumn{1}{l}{Light-} 		\\ [-3pt]
{Variable}\footnote{Observed by {\em NIFT}.}        &
{\it NIFT} & {12$\,\umu$m} & {25$\,\umu$m} & {60$\,\umu$m}
     & {100$\,\umu$m} &     {group} & \multicolumn{1}{r}{(d)}    &
	 \multicolumn{1}{l}{curve type}& {\em T$_0$\,(\rm{K})}  \\ 
 \hline
 TW Cam & 04166$+$5719 & 8.27   & 5.62 & 1.82  & $<$1.73   & A & \~85.6 & a & 555 \\
 RV Tau & 04440$+$2605 & 22.53  & 18.08& 6.40  & 2.52      & A & \~78.9 & b & 460 \\
 DY Ori & 06034$+$1354 & 12.44  & 14.93& 4.12  & $<$11.22  & B & \~60.3 &  & 295 \\
 CT Ori & 06072$+$0953 & 6.16   & 5.57 & 1.22  & $<$1.54   & B & 135.6 &  & 330 \\
 SU Gem & 06108$+$2734 & 7.90   & 5.69 & 2.16  & $<$11.66  & A & \~50.1 & b & 575 \\
 UY CMa & 06160$-$1701 & 3.51   & 2.48 & 0.57  & $<$1.00   & B & 113.9 & a & 420 \\
 U Mon  & 07284$-$0940 & 124.30 & 88.43& 26.28 & 9.24      & A & \~92.3 & b & 480 \\
 AR Pup & 08011$-$3627 & 131.33 & 94.32& 25.81 & 11.65     & B & \~75.0 & b & 450 \\
 IW Car & 09256$-$6324 & 101/06 & 96.24& 34.19 & 13.07     & B & \~67.5 & b & 395 \\
 GK Car & 11118$-$5726 & 2.87   & 2.48 & 0.78  & $<$12.13  & B & \~55.6 &  & 405 \\
 RU Cen & 12067$-$4508 & 5.36   & 11.02& 5.57  & 2.01      & B & \~64.7 &  & 255 \\
 SX Cen & 12185$-$4856 & 5.95   & 3.62 & 1.09  & $<$1.50   & B & \~32.9 & b & 590 \\
 AI Sco & 17530$-$3348 & 17.68  & 11.46& 2.88  & $<$45.62  & A & \~71.0 & b & 480 \\
 AC Her & 18281$+$2149 & 41.47  & 65.33& 21.12 & 7.79      & B & \~75.5 & a & 260 \\
 R Sct  & 18448$-$0545 & 20.88  & 9.30 & 8.10  & $<$138.78 & A & 140.2 & a \\
 R Sge  & 20117$+$1634 & 10.63  & 7.57 & 2.10  & $<$1.66   & A & \~70.6 & b & 455 \\
 V Vul  & 20343$+$2625 & 12.39  & 5.72 & 1.29  & $<$6.96   & A & \~75.7 & a & 690\\
\hline
\end{tabular*}
\end{minipage}
\vspace*{-6pt}
\end{table*}

\section[]{Material Description of the Envelope\break Predominantly Model}

If we assume that the dust grains in the envelope are  predominantly of
the same kind and are in thermal  equilibrium,\vadjust{\pagebreak} the luminosity at
frequency $\nu$ in the infrared is given by
\begin{equation}
   L(\nu)=\mskip-12mu\int\limits_{\rmn{envelope}}\mskip-12mu
   \rho(r)Q_{\rmn{abs}}(\nu)B[\nu,T_{\rmn{g}}(r)]\exp [-\tau(\nu,r)]\>
   \rmn{d}V,
\label{eq:luminosity}
\end{equation}
 where
 $Q_{\rmn{abs}}(\nu)$ is the absorption efficiency at frequency $\nu$,
 $\rho(r)$            is the dust grain density,
 $T_{\rmn{g}}(\nu)$    is the grain temperature,
 $B[\nu,T_{\rmn{g}}(r)]$  is the Planck function, and
 $\tau(\nu,r)$        is the optical depth at distance {\it r\/} from the
                      center of the star.
The temperature $T_{\rmn{g}}(r)$ is determined by the condition of energy
balance: amount of energy radiated = amount of energy absorbed. The
amount of energy absorbed at any point is proportional to the total
available energy at that point, which consists of:\vspace*{-6pt}
\begin{enumerate}
  \item The attenuated and diluted stellar radiation. The attenuated and diluted stellar radiation;
  \item Scattered radiation, and
  \item Reradiation from other grains.
\end{enumerate}

The amount of energy absorbed at any point is proportional to the total
available energy at that point
\begin{itemize}
  \item The attenuated and diluted stellar radiation. The attenuated and diluted stellar radiation;
  \item Scattered radiation, and
  \item Reradiation from other grains. Reradiation from other grains.
\end{itemize}
\begin{table}[b]
 \vspace*{-6pt}
 \centering
 \def\~{\hphantom{0}}
  \caption{It is for us, the living, rather to be
dedicated here to the unfinished work which, so nobly
carried out}
\label{t:tabletwo}
  \begin{tabular*}{\columnwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{}}
  \Hline
 & & \multicolumn{4}{c}{{Flux density (Jy)}}\\ [1pt]
\cline{3-7} \\ [-6pt]
{Name}        &  & & & & & {Sp.} \\ [-3pt]
{Variable}        
& {\it NIFT} & {12$\,\umu$m} & {25$\,\umu$m} & {60$\,\umu$m} & {100$\,\umu$m} &     {group} \\
 \hline
 TW Cam & 04166$+$5719 & 8.27   & 5.62 & 1.82  & $<$1.73   & A \\
 RV Tau & 04440$+$2605 & 22.53  & 18.08& 6.40  & 2.52      & A \\
 DY Ori & 06034$+$1354 & 12.44  & 14.93& 4.12  & $<$11.22  & B \\
 CT Ori & 06072$+$0953 & 6.16   & 5.57 & 1.22  & $<$1.54   & B \\
 SU Gem & 06108$+$2734 & 7.90   & 5.69 & 2.16  & $<$11.66  & A \\
 UY CMa & 06160$-$1701 & 3.51   & 2.48 & 0.57  & $<$1.00   & B \\
 U Mon  & 07284$-$0940 & 124.30 & 88.43& 26.28 & 9.24      & A \\
 AR Pup & 08011$-$3627 & 131.33 & 94.32& 25.81 & 11.65     & B \\
 IW Car & 09256$-$6324 & 101/06 & 96.24& 34.19 & 13.07     & B \\
 GK Car & 11118$-$5726 & 2.87   & 2.48 & 0.78  & $<$12.13  & B \\
 RU Cen & 12067$-$4508 & 5.36   & 11.02& 5.57  & 2.01      & B \\
 SX Cen & 12185$-$4856 & 5.95   & 3.62 & 1.09  & $<$1.50   & B \\
 AI Sco & 17530$-$3348 & 17.68  & 11.46& 2.88  & $<$45.62  & A \\
 AC Her & 18281$+$2149 & 41.47  & 65.33& 21.12 & 7.79      & B \\
 R Sct  & 18448$-$0545 & 20.88  & 9.30 & 8.10  & $<$138.78 & A \\
 R Sge  & 20117$+$1634 & 10.63  & 7.57 & 2.10  & $<$1.66   & A \\
 V Vul  & 20343$+$2625 & 12.39  & 5.72 & 1.29  & $<$6.96   & A \\
\hline
\end{tabular*}\vskip18pt
\end{table}

Detailed solutions of radiative transfer in circumstellar  dust
shells by \citet{b21} indicate that the effect of heating by
other grains becomes significant only at large optical depths at
the absorbing frequencies $[\tau(\rmn{UV})\gg 10]$, and at optical
depths $\tau(\rmn{UV})<1$ the grains have approximately the same
temperature that they would have if they were seeing the starlight
unattenuated and no other radiation.
\begin{description}
\item The Planck mean optical depths of circumstellar envelopes  around
several RV Tauri stars. 
\item The Planck mean optical depths of circumstellar envelopes  around
several RV Tauri stars. 
\item The Planck mean optical depths of circumstellar envelopes  around
several RV Tauri stars. 
\end{description}
The pure terrestrial silicates
or lunar silicates are found to be completely unsuitable to
account for the infrared emission from circumstellar dust shells
around M-type stars \citep{b21}. We assume that the absorption
efficiency $Q_{\rmn{abs}} (\nu)$ in the infrared varies as
$\nu^{\gamma}$. ${\gamma}=1$ appears to provide a reasonable fit
in a variety of sources \citep*{b11,b12}. Under these
circumstances the condition of energy balance implies that the
dust temperature $T_{\rmn{g}}$ will vary as $r^{\beta}$.

In view of the low value of the observed Planck mean  optical depth for
the stellar radiation and the nature of the assumed frequency
dependence of the absorption efficiency, the extinction of the infrared
radiation by the dust envelope can be neglected; see Table~\ref{t:tabletwo}. If we consider the
envelope to be spherically symmetric, (\ref{eq:luminosity}) reduces to
\begin{equation}
   L(\nu)=\!\!\int_{r_{1}}^{r_{2}}\!\!4\upi r^2\rho(r)\> Q_{\rmn{abs}}(\nu)B[\nu,T_{\rmn{g}}(r)]\> {\rmn{d}}r,
\label{eq:reducelum}
\end{equation}
where $r_1$ and $r_2$ are the inner and
outer radii of the shell. For a dusty density distribution
$\rho(r)\propto r^{\alpha}$ and $r_2\gg r_1$, (\ref{eq:reducelum}) reduces to
\begin{equation}
   L(\nu)\propto \nu^{2+\gamma-Q}\int_{X_0}^{\infty}{{x^Q}\over
   {\rmn{e}^x-1}}\rmn{d}x ,
\label{eq:dusty}
\end{equation}
where, in (\ref{eq:dusty}), $Q=-(\alpha+\beta+3)/\beta$ and $X_0=(h\nu
/kT_0)$. $T_0$ represents the temperature at the inner boundary of the
dust shell where grains start condensing. In a steady radiation
pressure driven mass outflow in the optically thin case, values of
$\alpha$ lie near $-2$ \citep{b8}. $\gamma$ and $\beta$ are related by
$\beta=-2/(\gamma+4)$.

In the {\it NIFT\/} Point Source Catalog \citep[PSC;][]{b2}, the flux
densities have been quoted at the effective wavelengths 12, 25, 60 and
\hbox{100\,$\umu$m}, assuming a flat energy spectrum $[\nu F(\nu)=1]$
for the observed sources. See Table~\ref{t:tablethree} for more
details. For each model given by equation~\ref{eq:dusty}, using the relative
system response, the color-correction factors in each of the {\it
NIFT\/} passbands were calculated and the fluxes were converted into
flux densities expected for a flat energy distribution, as assumed in
the {\it NIFT\/} PSC, so that the computed colors can be directly
compared with the colors determined from the catalog
quantities. Such a procedure is more appropriate than correcting the
{\it NIFT\/} colors for the energy distribution given by a particular
model and then comparing them with those computed by the model.\vspace*{-6pt}

\begin{table*}
 \centering
 \def\~{\hphantom{0}}
 \begin{minipage}{130mm}
  \caption{It is for us, the living, rather to be
dedicated here to the unfinished work which, so nobly
carried out}
\label{t:tablethree}
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{}}
  \Hline
 & & \multicolumn{4}{c}{{Flux density (Jy)} \footnote{Observed by {\em NIFT}.}}\\ [1pt]
\cline{3-7} \\ [-6pt]
{Name}        &  & & & & & {Sp.} & \multicolumn{1}{r}{Period}& \multicolumn{1}{l}{Light-} 		\\ [-3pt]
{Variable}\footnote{Observed by {\em NIFT}.}        &
{\it NIFT} & {12$\,\umu$m} & {25$\,\umu$m} & {60$\,\umu$m}
     & {100$\,\umu$m} &     {group} & \multicolumn{1}{r}{(d)}    &
	 \multicolumn{1}{l}{curve type}& {\em T$_0$\,(\rm{K})}  \\ 
 \hline
 TW Cam & 04166$+$5719 & 8.27   & 5.62 & 1.82  & $<$1.73   & A & \~85.6 & a & 555 \\
 RV Tau & 04440$+$2605 & 22.53  & 18.08& 6.40  & 2.52      & A & \~78.9 & b & 460 \\
 DY Ori & 06034$+$1354 & 12.44  & 14.93& 4.12  & $<$11.22  & B & \~60.3 &  & 295 \\
 CT Ori & 06072$+$0953 & 6.16   & 5.57 & 1.22  & $<$1.54   & B & 135.6 &  & 330 \\
 SU Gem & 06108$+$2734 & 7.90   & 5.69 & 2.16  & $<$11.66  & A & \~50.1 & b & 575 \\
 UY CMa & 06160$-$1701 & 3.51   & 2.48 & 0.57  & $<$1.00   & B & 113.9 & a & 420 \\
 U Mon  & 07284$-$0940 & 124.30 & 88.43& 26.28 & 9.24      & A & \~92.3 & b & 480 \\
 AR Pup & 08011$-$3627 & 131.33 & 94.32& 25.81 & 11.65     & B & \~75.0 & b & 450 \\
 IW Car & 09256$-$6324 & 101/06 & 96.24& 34.19 & 13.07     & B & \~67.5 & b & 395 \\
 GK Car & 11118$-$5726 & 2.87   & 2.48 & 0.78  & $<$12.13  & B & \~55.6 &  & 405 \\
 RU Cen & 12067$-$4508 & 5.36   & 11.02& 5.57  & 2.01      & B & \~64.7 &  & 255 \\
 SX Cen & 12185$-$4856 & 5.95   & 3.62 & 1.09  & $<$1.50   & B & \~32.9 & b & 590 \\
 AI Sco & 17530$-$3348 & 17.68  & 11.46& 2.88  & $<$45.62  & A & \~71.0 & b & 480 \\
 AC Her & 18281$+$2149 & 41.47  & 65.33& 21.12 & 7.79      & B & \~75.5 & a & 260 \\
 R Sct  & 18448$-$0545 & 20.88  & 9.30 & 8.10  & $<$138.78 & A & 140.2 & a \\
 R Sge  & 20117$+$1634 & 10.63  & 7.57 & 2.10  & $<$1.66   & A & \~70.6 & b & 455 \\
 V Vul  & 20343$+$2625 & 12.39  & 5.72 & 1.29  & $<$6.96   & A & \~75.7 & a & 690\\
\hline
\end{tabular*}
\end{minipage}
\vspace*{-6pt}
\end{table*}

\section{An Example of Head One Color-Color Diagram An Example of Head One Color-Color Diagram}
\subsection{An Example of Head Two: Color-Color Diagram An Example of Head Two: Color-Color Diagram}
\label{ss:example}

The IR color is defined as
%\[
\begin{eqnarray*}
  [\nu_1]-[\nu_2]=-2.5\log [f(\nu_1)/f(\nu_2)],
\end{eqnarray*}
%\]
 where $\nu_1$ and $\nu_2$ are any two wavebands and $f(\nu_1)$ and
$f(\nu_2)$ are the corresponding flux densities assuming a flat energy
spectrum for the source. In Figure~\ref{f:mouse1column}, we have
plotted the [25]--[60] colors of RV Tauri stars against their
corresponding [12]--[25] colors derived from the {\it NIFT\/}
data. Filled circles represent stars of group A and open circles stars
of group B. \vspace*{6pt}
\begin{longequation}
\left(\begin{array}{cc}%
[\tau_i(D-\alpha_iW]^{-1}+(\eta_0I+\eta_1W)[\tau_2(D-\alpha_2W)]^{-1}(\eta_0I+\eta_1W)&
(\eta_0I+\eta_1W)[\tau_2(D-\alpha_2W)]^{-1}\\
{[}\tau_2(D-\alpha_2W)]^{-1}(\eta_0I+\eta_1W)&[\tau_2(D-\alpha_2W)]^{-1}
\end{array}
\right).
\label{eq:long} 
\end{longequation}\vskip6pt 
Equation~(\ref{eq:long}) is a long equation.  The two sets of
near-parallel lines represent the loci of constant inner shell
temperature $T_0$ and the quantity $Q$ defined above. The models
correspond to the case of absorption efficiency $Q_{\rmn{abs}}(\nu)$
varying as $\nu$ (with $\gamma=1$ and hence $\beta=-0.4$). We have
omitted R Sct in Figure~\ref{f:mouse1column} because it shows a large
deviation from the average relation shown by all the other objects. R
Sct has a comparatively large excess at 60$\,\umu$m, but the extent of
a possible contamination by the infrared cirrus \citep{b16} is
unknown.  \citet{b9} found no evidence of the presence of a dust
envelope at near-IR wavelengths and the spectrum was consistent with a
stellar continuum. This explains why R Sct lies well below the mean
relation shown by stars of groups A and C between the [3.6]--[11.3]
color excess and the photometrically determined (Fe/H) \citep{b4}. R
Sct has the longest period of 140$\,$d among the RV Tauri stars
detected at far-infrared wavelengths and does the RV Tauri stars
detected at far-infrared wavelengths and does the RV Tauri stars
detected at far-infrared wavelengths and does not have the 10-$\umu$m
emission feature seen in other objects \citep{b5,b19}. R Sct is
probably the most irregular RV Tauri star known \citep{b17}.  In Web
Appendix 1, we give a derivation that shows that this is to be
expected.

The inner shell temperatures $(T_0)$ derived for the various objects
are also given in Table~\ref{t:tableone} and we find the majority
of them to have temperatures in the narrow range
400--600$\,$K. If the dependences of $Q_{\rmn{abs}}(\nu)$ on $\nu$ and
$\rho(r)$ on $r$ are similar in all the objects considered, then in
the color--color diagram they all should lie along a line
corresponding to different values of $T_0$ and in
Figure~\ref{f:bigmouse} we find that this is ebiomntially the case. In
view of the quoted uncertainties in the flux measurements, we cannot
attach much significance to the scatter in Figure~\ref{f:bigmouse}.

\begin{figure}
 \centerline{\includegraphics[width=2.25in]{mouse.eps}}
\caption{An example of figure caption. An example of figure
caption. An example of figure caption. An example of figure
caption.}
\label{f:mouse1column}
\end{figure}

At \hbox{100\,$\umu$m} the infrared sky is characterized by emission,
called infrared cirrus, from interstellar dust on all spatial scales
\citep{b16}, thereby impairing the measurements at far-infrared
wavelengths. \eqnbreaktop{3pc} In Figure~\ref{f:shortmouse}, we have plotted the
[60]--[100] colors of the six RV Tauri stars detected at
\hbox{100\,$\umu$m} against their [25]--[60] colors, along with the
grid showing the regions of different values for inner shell
temperature $T_0$ and the quantity $Q$, as in Figure~\ref{f:bigmouse}.
The results indicated by Figure~\ref{f:shortmouse} are consistent with
those derived from Figure~\ref{f:mouse1column}.  AR Pup shows a large
excess at \hbox{100\,$\umu$m} but, in view of the large values for the
cirrus flags given in the catalog, the intrinsic flux at
\hbox{100\,$\umu$m} is uncertain.

\subsection{Radial Distribution of Dust}

From Figure~\ref{f:shortmouse}, it is evident that all RV Tauri stars
lie between the lines corresponding to $Q=1.5$ and 0.5. With
 \[
  \alpha=-(1+Q)\beta-3,
 \]
 these values suggest limits of $r^{-2.0}$ and $r^{-2.4}$ for the dust
density variation, indicating a near-constant mass-loss rate.
\citet{b12} has suggested that the density in the circumstellar
envelope around RV Tauri stars varies as $r^{-1}$, implying a
mass-loss rate that was greater in the past than it is currently.  By
fitting a power law to the observed fluxes, such that $f(\nu)$ varies
as $\nu^q$, values of $q$ determined by him for the various objects
given in Table~\ref{t:tableone} lie in the range 0.6--1.2, with a mean
$\skew5\bar q=0.98$. The assumption of a power law corresponds to the
case of $X_0=0$ in equation (3) and hence we get
 \[
  q=2+\gamma -Q.
 \]
Since we assume that $Q_{\rmn{abs}}(\nu)$ varies as $\nu$, the
resulting value for $Q$=2.0. None of the objects is found to lie in the
corresponding region in the color--color diagram. Even this extreme
value for $Q$ implies a density which varies as $r^{-1.8}$.

\citet{b9} have reported that the simultaneous optical and near-IR
data of AC Her can be fitted by a combination of two blackbodies
at 5680 and 1800\,K, representing, respectively, the stellar and
dust shell temperatures, and suggested that in RV Tauri stars the
grain formation is a sporadic phenomenon and not a continuous
process. Apparently, they have been influenced by the remark by
\citet{b7} that their data in the 3.5--11$\,\umu$m region of AC
Her indicated a dust temperature of $\sim$300\,K. We find that the
{\it K--L\/} colors given by \citet{b5} and
\citet{b9} are all consistent with each other. Surely, hot dust
($\sim$1800\,K), if present at the time of observations by
\citet{b9}, would have affected the {\it K--L\/} color
significantly. AC Her, like other members of its class, is found
to execute elongated loops in the ({\it U--B\/}), ({\it B--V\/})
plane \citep{b20}, indicating that significant departure of the
stellar continuum from the blackbody is to be expected. Further,
their data show only a marginal excess at the near-IR wavelengths.\vspace*{-4pt}
\begin{enumerate}
\item[{\it Step} 1:] The attenuated and diluted stellar radiation;
\item[{\it Step} 2:] Scattered radiation, and
\item[{\it Step} 3:] Reradiation from other grains.\vspace*{-8pt}
\end{enumerate}

\enlargethispage{-2pt}

\subsection{An Example of Head two}
\subsubsection{An example of head three comparison with oxygen and~carbon~Miras}

In Figure~\ref{f:shortmouse} we have also shown the positions of a
sample of oxygen-rich and carbon-rich Miras.  We feel that the case
for the existence of hot dust around AC Her and hence for the sporadic
grain formation around RV Tauri stars is not strong. In
Figure~\ref{f:bigmouse}, we find that AC Her and RU Cen lie very close
to R Sct which, according to \citet{b9}, shows no evidence for the
presence of a hot dust envelope. At the low temperatures
characteristic of the Miras, a part of the emission at 12$\,\umu$m
comes from the photosphere.  For a blackbody at 2000$\,$K, the ratio
of fluxes at wavelengths of 12 and 2$\,\umu$m $(f_{12}/f_{2})\sim
0.18$. The Miras shown in Figure~\ref{f:bigmouse} have
$(f_{12}/f_{2})$ ratios larger than twice the above value. It is clear
that the three groups of objects populate three different regions of
the diagram. \citet{b10} have already noticed that there are distinct
differences between the {\it NIFT\/} colors of oxygen-rich and
carbon-rich objects. On the basis of an analysis, using a bigger
sample of bright giant stars in the {\it NIFT\/} catalog, this has
been interpreted by \citet{b25} as being due to a systematic
difference in the dust grain emissivity index.

\begin{figure*}
  \centerline{\includegraphics[width=4.5in]{mouse.eps}}
  \caption{An example of figure caption. An example of 
  figure caption. An example of figure caption. An example of
   figure caption. An example of figure caption.}
\label{f:bigmouse}
\end{figure*}

\looseness-1U Mon shows the 10-$\umu$m silicate emission convincingly and, in
most of the other objects for which low-resolution spectra in the
near-infrared have been reported \citep{b5,b19}, the 10-$\umu$m
emission may be partly attributed to silicates. Hence it is
reasonable to expect that, in the envelopes around at least some
of the RV Tauri stars, the dust grains are predominantly of
silicates, as in the case of oxygen Miras \citep{b21}. The fact
that none of the RV Tauri stars is found in the region of the
two-color diagram occupied by the oxygen Miras indicates that the
emissivity indices of the silicate grains in the two cases are
different. Because of the higher temperatures and luminosities,
the environment of grain formation will be different in RV Tauri
stars.
\begin{figure}[b]
  \centerline{\includegraphics[width=2in]{mouse.eps}}
  \caption{An example of short figure caption.}
\vspace*{-3pt}
\label{f:shortmouse}
\end{figure}

\paragraph{Correlation with subgroups}%
\citet{b20} have identified three spectroscopic subgroups, which
are designated as groups A, B and C. Objects of group A are
metal-rich; group C are metal-poor; group B objects are also
metal-poor, but  show carbon enhancements \citep{b20,b14,b4,b1}.\vspace*{-6pt}
\begin{theorem}
It is interesting to see that Table~\ref{t:tableone} contains no group
C objects and that in Figure~\ref{f:shortmouse} there is a clear
separation of the two spectroscopic subgroups A and B, with the
demarcation occurring at an inner shell temperature of about 450$\,$K,
group B stars having lower temperatures than group A.
\end{theorem}
\begin{proof}
It is interesting to see that Table~\ref{t:tableone} contains no group
C objects and that in Figure~\ref{f:shortmouse} there is a clear
separation of the two spectroscopic subgroups A and B, with the
demarcation occurring at an inner shell temperature of about 450$\,$K,
group B stars having lower temperatures than group A.
\end{proof}
It is interesting to see that Table~\ref{t:tableone} contains no group
C objects and that in Figure~\ref{f:shortmouse} there is a clear
separation of the two spectroscopic subgroups A and B, with the
demarcation occurring at an inner shell temperature of about 450$\,$K,
group B stars having lower temperatures than group A. SX Cen is the
only exception. \citet{b14} has reported that metal lines are stronger
in SX Cen than in other group B objects. It may be worth noting that
SX Cen has the shortest period among the 100 or so objects with the RV
Tauri classification. RU Cen has the coolest inner shell temperature,
as already suggested by the near-infrared spectrum\break \citep{b6}.

\begin{sidewaystable}
 \centering
 \def\~{\hphantom{0}}
% \begin{minipage}{225mm}
  \hsize\textheight
  \caption{It is for us, the living, rather to be
dedicated here to the unfinished work which, so nobly
carried out}
\label{t:sidetable}
\hskip-12pt\begin{tabular*}{\textheight}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\hskip12pt}}
  \Hline
 & & \multicolumn{4}{c}{{Flux density (Jy)} \footnote{Observed by {\em NIFT}.}}\\ [1pt]
\cline{3-7} \\ [-6pt]
{Name}        &  & & & & & {Sp.} & \multicolumn{1}{r}{Period}& \multicolumn{1}{l}{Light-} 		\\ [-3pt]
{Variable}\footnote{Observed by {\em NIFT}.}        &
{\it NIFT} & {12$\,\umu$m} & {25$\,\umu$m} & {60$\,\umu$m}
     & {100$\,\umu$m} &     {group} & \multicolumn{1}{r}{(d)}    &
	 \multicolumn{1}{l}{curve type}& {\em T$_0$\,(\rm{K})}  \\ 
 \hline
 TW Cam & 04166$+$5719 & 8.27   & 5.62 & 1.82  & $<$1.73   & A & \~85.6 & a & 555 \\
 CT Ori & 06072$+$0953 & 6.16   & 5.57 & 1.22  & $<$1.54   & B & 135.6 &  & 330 \\
 SU Gem & 06108$+$2734 & 7.90   & 5.69 & 2.16  & $<$11.66  & A & \~50.1 & b & 575 \\
 UY CMa & 06160$-$1701 & 3.51   & 2.48 & 0.57  & $<$1.00   & B & 113.9 & a & 420 \\
 U Mon  & 07284$-$0940 & 124.30 & 88.43& 26.28 & 9.24      & A & \~92.3 & b & 480 \\
 AR Pup & 08011$-$3627 & 131.33 & 94.32& 25.81 & 11.65     & B & \~75.0 & b & 450 \\
 IW Car & 09256$-$6324 & 101/06 & 96.24& 34.19 & 13.07     & B & \~67.5 & b & 395 \\
 RU Cen & 12067$-$4508 & 5.36   & 11.02& 5.57  & 2.01      & B & \~64.7 &  & 255 \\
 SX Cen & 12185$-$4856 & 5.95   & 3.62 & 1.09  & $<$1.50   & B & \~32.9 & b & 590 \\
 AI Sco & 17530$-$3348 & 17.68  & 11.46& 2.88  & $<$45.62  & A & \~71.0 & b & 480 \\
 AC Her & 18281$+$2149 & 41.47  & 65.33& 21.12 & 7.79      & B & \~75.5 & a & 260 \\
 R Sct  & 18448$-$0545 & 20.88  & 9.30 & 8.10  & $<$138.78 & A & 140.2 & a \\
 R Sge  & 20117$+$1634 & 10.63  & 7.57 & 2.10  & $<$1.66   & A & \~70.6 & b & 455 \\
\hline
\end{tabular*}
%\end{minipage}
\end{sidewaystable}

\subsubsection{Correlation with subgroups}%
\paragraph{Head four correlation with subgroups}%
Group B objects follow a different mean relationship from those of
group A, having systematically larger 11-$\umu$m excess for a given
excess at 3$\,\umu$m. For a general sample of RV Tauri stars, the
distinction between the oxygen-rich and carbon-rich objects is not
that apparent in the {\it JHKL\/} bands. In Figure~\ref{f:shortmouse}
we have plotted the near-IR magnitudes of the objects given in
Table~\ref{t:sidetable} (except V Vul which has no available
measurements) in the {\it J--K, K--L\/} plane. The colors, taken from
\citet{b9}, are averaged if more than one observation exists, because
the internal agreements are found to be often of the order of
observational uncertainties, in accordance with the earlier finding by
\citet{b5} that variability has relatively little effect on
colors. Barring RU Cen and AC Her, it is evident that stars belonging
to group B show systematically larger excebioms at {\it L\/} band for
a given excess at {\it K}. The low excebioms at near-IR wavelengths
for AC Her and RU Cen are consistent with the very low dust
temperatures indicated by the far-infrared colors.
%

It is already well established that from {\it UBV\/} photometry one
can distinguish between groups A and B, members of group A being
significantly redder than those of group B \citep{b20}.  Similarly,
\citet{b4} has found that the two spectroscopic groups are well
separated in the DDO color--color diagrams when mean colors are
used for the individual objects. The clear separation of the
spectroscopic subgroups A and B in the IR two-color diagram suggests
that the natures of dust grains in the envelopes in the two cases are
not identical. This is to be expected because of the differences in
the physical properties of the stars themselves. The average colors
of group B stars are bluer than group A, but the envelope dust
temperatures of B are cooler than those of A. The near-IR spectra of
AC Her and RU Cen are extremely similar \citep{b6}. The striking
similarities in the optical spectra of AC Her and RU Cen have been
pointed out by Bidelman \citep{b18}. We feel that the physical
properties, including the chemical composition, of the grains formed
in the circumstellar envelope strongly depend on those of the embedded
star. This, probably, explains the diversity of the energy
distributions of RV Tauri stars in the near-infrared found by
\citet{b6}. On the basis of the observed differences in chemical
abundances and space distribution of RV Tauri stars {\tt
http://www.duke.edu/$\sim$delon001/Biometrics\_tables.pdf}.  See
Section~\ref{s:discuss} for further discussion.

\citet{b13} have subdivided RV Tauri stars into two clabioms, RVa and
RVb, on the basis of their light curves; the former shows a constant
mean brightness, whereas the latter shows a cyclically varying mean
brightness. Extensive observations in the near-infrared show that, on
average, RVb stars are redder than RVa stars, In RVb stars dust shells
are denser in the inner regions and hence radiate strongly in the
1--3$\,\umu$m region. Figure~\ref{f:shortmouse} confirms this; RVb
objects show systematically larger ({\it J--K\/}) and ({\it K--L\/})
colors than RVa objects. Apparently, there is no distinction between
objects of the two light-curve types at far-infrared wavelengths
(Figure~\ref{f:shortmouse}).

\section{Discussion}
\label{s:discuss}

In the [12]--[25], [25]--[60] color diagram, RV Tauri stars populate
cooler temperature regions $(T<600 \,\rmn{K})$, distinctly different from
those occupied by the oxygen and carbon Miras. Using a simple model
in which
\begin{enumerate}
  \item[1.] the envelope is spherically symmetric,
  \item[2.] the IR-emitting grains are predominantly of the same kind, and
  \item[3.] in the infrared the absorption efficiency $Q_{\rmn{abs}}
        (\nu)\propto\nu$,
\end{enumerate}
we find that the {\it NIFT\/} fluxes are consistent with the
density in the envelope $\rho(r)\propto r^{-2}$, where {\it r\/}
is the radial distance. Such a dependence for the dust density
implies that the mass-loss rates in RV Tauri stars have not
reduced considerably during the recent past, contrary to the
suggestion by \citet{b12}. In the two-color diagram, the
blackbody line and the line corresponding to $\rho(r)\propto
r^{-2.2}$ nearly overlap and the present data are insufficient to
resolve between the two cases. The latter case is more physically
reasonable, however.

\backmatter

%%%%%% include this section if you wish to acknowledge people,
%%%%%% grant support, etc.

\section*{Acknowledgements}

The authors thank Professor A. Sen for some helpful suggestions,
Dr C. R. Rangarajan for a critical reading of the original version of the
paper, and an anonymous referee for very useful comments that improved
the presentation of the paper.\vspace*{-8pt}

%%%%%% include this section only if your manuscript refers to supplementary
%%%%%% materials -- see Instructions for Authors at 
%%%%%% http://www.tibs.org/biometrics

\section*{Supplementary Materials}

Web Appendix 1 referenced in Section~\ref{ss:example} is available
with this paper at the Biometrics website on Wiley Online Library.
\vspace*{-8pt}

\begin{thebibliography}{}
\bibitem[\protect\citeauthoryear{Akash and Tirky}{1988}]{b24} 
Akash, F. J. and Tirky, T. (1988). Proper multivariate conditional
autoregressive models for spatial data analysis. {\it Biometrics} {\bf 196,} 173.

\bibitem[\protect\citeauthoryear{Balaram et~al.}{1985a}]{b2} 
Balaram, C. A., Neeraj, G., Haq, H. J., and Cliff, P. E., (1985a). {\it
NIFT\/} 2nd edition. Boca Raton, Florida: Chapman and Hall.

\bibitem[\protect\citeauthoryear{Commel}{1961}]{b18} 
Commel, J. K. (1961). {\it National Sangget Academia}, 2nd edition.
Hoboken, New Jersey: Wiley.

\bibitem[\protect\citeauthoryear{Das  and Patra}{1986}]{b25} 
Das, B. and Patra, H. M. (1986). Using counts to simultaneously estimate
abundance and detection probabilities in a salamander community. {\it
Herpetologica} {\bf 60,} 468--478.

\bibitem[\protect\citeauthoryear{Emrat}{1974}]{b14} Emrat, T. (1974).
{\it Topics in Stochastic Processes.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Emrat}{1985}]{b15} Emrat, T. (1985).
{\it Topics in Stochastic Processes.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Goldman et~al.}{1987}]{b9} 
Goldman, M. J. and Ewin, A. (1987). A comparison of smoothing
techniques for CD4 data measured with error in a time-dependent Cox
proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2061--2077.

\bibitem[\protect\citeauthoryear{Goodsman}{1972}]{b8} 
Goodsman, R. C. (1972). Testing hypotheses in the functional linear
model. {\it Scandinavian Journal of Statistics} {\bf 30,} 241--251.

\bibitem[\protect\citeauthoryear{Gooms}{1972}]{b5} Gooms, R. D.
(1972). Goodsman, R.C. (1972). Testing hypotheses in the functional linear
model. {\it Scandinavian Journal of Statistics} {\bf 31,} 315--323.

\bibitem[\protect\citeauthoryear{Gooms  and Wool}{1970}]{b7} Gooms,
R. D. and Wool, N. J. (1970). A comparison of smoothing
techniques for CD4 data measured with errors in a time-dependent Cox
proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2091--2099.

\bibitem[\protect\citeauthoryear{Hackel}{1985}]{b10} 
Hackel, P. (1985). {\it Topics in Stochastic Processes.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{\nobreak Holloman, \nobreak Tinku,  and Gerg}{Holloman et~al.}{1979}]{b11}
Holloman, P. M., Tinku, H. A., and Gerg, I. (1979). A comparison of smoothing
techniques for CD4 data measured with techniques a time-dependent Cox
proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2105--2111.

\bibitem[\protect\citeauthoryear{Juman}{1986}]{b12} 
Juman, M. (1986). Using counts to simultaneously estimate
abundance and detection probabilities in a salamander community. {\it
Herpetologica} {\bf 61,} 482--495.

\bibitem[\protect\citeauthoryear{Kartik B}{1969}]{b13} 
Kartik, B. V. (1969). Using counts to simultaneously estimate
abundance and detection probabilities in a salamander community. {\it
Herpetologica} {\bf 62,} 511--519.

\bibitem[\protect\citeauthoryear{Lenin}{1932}]{b17} 
Lenin, D. B. (1932). A comparison of smoothing
techniques for CD4 data measured with errors in a time-dependent Cox
proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2125--2135.

\bibitem[\protect\citeauthoryear{O'Rourke}{1979}]{b4} O'Rourke, D. (1996). Industrial ecology: A 
critical review. {\it International Journal of Environment and Pollution}
{\bf 6,} 389--112.

\bibitem[\protect\citeauthoryear{Oman and \nobreak Raj}{1986}]{b19}
Oman, F. M. and  Raj, E. (1986). {\it Topics in Stochastic Process.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Prem et~al.}{1963}]{b20} Prem, G. W., Christ, W., Smap, J.,
Wills, J. A. (1963). {\it Topics in Stochastic Processes.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Rahul}{1981}]{b1} Rahul, S. R. (1981).
Industrial ecology: A  critical review. {\it International Journal of
Environment and Pollution} {\bf 6,} 371--375.

\bibitem[\protect\citeauthoryear{Ram  and Shyam}{1972}]{b6} Ram, R. D.
and Shyam, S. (1972). {\it Topics in Stochastic Process.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Ravan  and Hari}{1983a}]{b21} Ravan,
M. and Hari, S. (1983). Industrial ecology: A  critical review.
{\it International Journal of Environment and Pollution} {\bf 6,} 389--395.

\bibitem[\protect\citeauthoryear{Ravan  and Hari}{1983b}]{b22}
Ravan, M. and Hari, S. (1984). Industrial ecology: A  critical
review. {\it International Journal of Environment and Pollution} {\bf 7,} 512--519.

\bibitem[\protect\citeauthoryear{Sharma et~al.}{1984}]{b16} Sharma,
F. J. (1984). {\it Topics in Stochastic Process.} New York: Academic Press.

\bibitem[\protect\citeauthoryear{Vim   and Potter}{1988}]{b23} Vim, W.
E. and Potter, H. J. (1988). A  critical
review. {\it International Journal of Environment and Pollution} {\bf 9,} 635--641.

\end{thebibliography}

\appendix

\section{}
\subsection{Computation of E$_i\{\alpha_i\}$}

(This appendix was not part of the original paper by
A.V.~Raveendran and is included here just for illustrative
purposes. The references are not relevant to the text of the
appendix, they are references from the bibliography used to
illustrate text before and after citations.)

Here is an equation; note how it is numbered:
\begin{equation}
A = B+C. 
\label{eq:appeq}
\end{equation}
Equation~(\ref{eq:appeq}) is an the only numbered equation in this appendix.

Spectroscopic observations of bright quasars show that the mean
number density of Ly$\alpha$ forest lines, which satisfy certain
criteria, evolves like $\rmn{d}N/\rmn{d}z=A(1+z)^\gamma$, where
$A$ and~$\gamma$ are two constants.  Given the above intrinsic
line distribution we examine the probability of finding large gaps
in the Ly$\alpha$ forests.  We concentrate here only on the
statistics and neglect all observational complications such as the
line blending effect \citep[see][for example]{b11}. We concentrate here only on the
statistics and neglect all observational complications such as the
line blending effect \citep[see][for example]{b11}. We concentrate here only on the
statistics and neglect all observational complications such as the
line blending effect \citep[see][for example]{b11}.

The references are not relevant to the text of the
appendix, they are references from the bibliography used to
illustrate text before and after citations.)

Spectroscopic observations of bright quasars show that the mean
number density of Ly$\alpha$ forest lines, which satisfy certain
criteria, evolves like $\rmn{d}N/\rmn{d}z=A(1+z)^\gamma$, where
$A$ and~$\gamma$ are two constants.  Given the above intrinsic
line distribution we examine the probability of finding large gaps
in the Ly$\alpha$ forests.  We concentrate here only on the
statistics and neglect all observational complications such as the
line blending effect \citep[see][for example]{b11}. We concentrate here only on the
statistics and neglect all observational complications such as the
line blending effect \citep[see][for example]{b11}. We concentrate here only on the
statistics and neglect all observational complications such as the
line blending effect \citep[see][for example]{b11}. \vadjust{\vfill\pagebreak}

Suppose we have observed a Ly$\alpha$ forest between redshifts $z_1$
and~$z_2$ and found $N-1$ lines.  For high-redshift quasars $z_2$~is
usually the emission redshift $z_{\rmn{em}}$ and $z_1$ is set to
$(\lambda_{\rmn{Ly}\beta}/\lambda_{\rmn{Ly}\alpha})(1+z_{\rmn{em}})=0.844
(1+z_{\rmn{em}})$ to avoid contamination by Ly$\beta$ lines.  We
want to know whether the largest gaps observed in the forest are
significantly inconsistent with the above line distribution.  To do
this we introduce a new variable~$x$:\vspace*{1.5pt}
%
\[
x={(1+z)^{\gamma+1}-(1+z_1)^{\gamma+1} \over
     (1+z_2)^{\gamma+1}-(1+z_1)^{\gamma+1}}.
\]
\vskip1.5pt%
$x$ varies from 0 to 1.  We then have $\rmn{d}N/\rmn{d}x=\lambda$,
where $\lambda$ is the mean number of lines between $z_1$ and $z_2$
and is given by
%
\[%
\lambda\equiv{A[(1+z_2)^{\gamma+1}-(1+z_1)^{\gamma+1}]\over\gamma+1}.
\]
%
This means that the Ly$\alpha$ forest lines are uniformly
distributed in~$x$.
%
\label{lastpage}

\end{document}

### 2012-07-31 paper/example/biomsample_bib.tex
Paper style file

--- 2012-07-31 paper/example/biomsample.tex
@@
-% biomsample.tex
+% biomsample_bib.tex
 %
@@
 % \usepackage{Times}
-
 %%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
-
 \def\bSig\mathbf{\Sigma}
@@
 \newcommand{\tr}{\mbox{tr}}
-
-%  If you have a landscape table you need to use the rotating package
 
@@
 emission far in excess of their expected blackbody continuum, arising
-from their extended cool dust envelopes \citep{b7,b5,b6}. Recently,
-\citep{b9} have given detailed descriptions of the near-infrared
+from their extended cool dust envelopes \citep{b1,b2,b3}. Recently,
+\citep{b4} have given detailed descriptions of the near-infrared
 properties of RV Tauri stars. In this paper we present an analysis of
 the {\it NIFT\/} data of RV Tauri stars with the help of the
-far-infrared two-color diagram and a grid computed using a simple
-model of the dust envelope. Such two-color plots have already been
+far-infrared two-colour diagram and a grid computed using a simple
+model of the dust envelope. Such two-colour plots have already been
 employed extensively by several investigators to study the
@@
 objects which are in the late stages of stellar evolution
-\citep{b10,b25,b24,b23}.
+\citep{b5}.
 
@@
  $\tau(\nu,r)$        is the optical depth at distance {\it r\/} from the
-                      center of the star.
+                      centre of the star.
 The temperature $T_{\rmn{g}}(r)$ is determined by the condition of energy
@@
 details. For each model given by equation~\ref{eq:dusty}, using the relative
-system response, the color-correction factors in each of the {\it
+system response, the colour-correction factors in each of the {\it
 NIFT\/} passbands were calculated and the fluxes were converted into
 flux densities expected for a flat energy distribution, as assumed in
-the {\it NIFT\/} PSC, so that the computed colors can be directly
-compared with the colors determined from the catalog
+the {\it NIFT\/} PSC, so that the computed colours can be directly
+compared with the colours determined from the catalogue
 quantities. Such a procedure is more appropriate than correcting the
-{\it NIFT\/} colors for the energy distribution given by a particular
+{\it NIFT\/} colours for the energy distribution given by a particular
 model and then comparing them with those computed by the model.\vspace*{-6pt}
@@
 
-\section{An Example of Head One Color-Color Diagram An Example of Head One Color-Color Diagram}
-\subsection{An Example of Head Two: Color-Color Diagram An Example of Head Two: Color-Color Diagram}
+\section{An Example of Head One Colour-Colour Diagram An Example of Head One Colour-Colour Diagram}
+\subsection{An Example of Head Two: Colour-Colour Diagram An Example of Head Two: Colour-Colour Diagram}
 \label{ss:example}
 
-The IR color is defined as
-%\[
-\begin{eqnarray*}
+The IR colour is defined as
+\[
   [\nu_1]-[\nu_2]=-2.5\log [f(\nu_1)/f(\nu_2)],
-\end{eqnarray*}
-%\]
+\]
  where $\nu_1$ and $\nu_2$ are any two wavebands and $f(\nu_1)$ and
@@
 spectrum for the source. In Figure~\ref{f:mouse1column}, we have
-plotted the [25]--[60] colors of RV Tauri stars against their
-corresponding [12]--[25] colors derived from the {\it NIFT\/}
+plotted the [25]--[60] colours of RV Tauri stars against their
+corresponding [12]--[25] colours derived from the {\it NIFT\/}
 data. Filled circles represent stars of group A and open circles stars
@@
 Sct has a comparatively large excess at 60$\,\umu$m, but the extent of
-a possible contamination by the infrared cirrus \citep{b16} is
+a possible contamination by the infrared cirrus \citep{b15,b16} is
 unknown.  \citet{b9} found no evidence of the presence of a dust
@@
 relation shown by stars of groups A and C between the [3.6]--[11.3]
-color excess and the photometrically determined (Fe/H) \citep{b4}. R
+colour excess and the photometrically determined (Fe/H) \citep{b4}. R
 Sct has the longest period of 140$\,$d among the RV Tauri stars
@@
 $\rho(r)$ on $r$ are similar in all the objects considered, then in
-the color--color diagram they all should lie along a line
+the colour--colour diagram they all should lie along a line
 corresponding to different values of $T_0$ and in
@@
 wavelengths. \eqnbreaktop{3pc} In Figure~\ref{f:shortmouse}, we have plotted the
-[60]--[100] colors of the six RV Tauri stars detected at
-\hbox{100\,$\umu$m} against their [25]--[60] colors, along with the
+[60]--[100] colours of the six RV Tauri stars detected at
+\hbox{100\,$\umu$m} against their [25]--[60] colours, along with the
 grid showing the regions of different values for inner shell
@@
 excess at \hbox{100\,$\umu$m} but, in view of the large values for the
-cirrus flags given in the catalog, the intrinsic flux at
+cirrus flags given in the catalogue, the intrinsic flux at
 \hbox{100\,$\umu$m} is uncertain.
@@
 
-From Figure~\ref{f:shortmouse}, it is evident that all RV Tauri stars
+>From Figure~\ref{f:shortmouse}, it is evident that all RV Tauri stars
 lie between the lines corresponding to $Q=1.5$ and 0.5. With
@@
 resulting value for $Q$=2.0. None of the objects is found to lie in the
-corresponding region in the color--color diagram. Even this extreme
+corresponding region in the colour--colour diagram. Even this extreme
 value for $Q$ implies a density which varies as $r^{-1.8}$.
@@
 Her indicated a dust temperature of $\sim$300\,K. We find that the
-{\it K--L\/} colors given by \citet{b5} and
+{\it K--L\/} colours given by \citet{b5} and
 \citet{b9} are all consistent with each other. Surely, hot dust
 ($\sim$1800\,K), if present at the time of observations by
-\citet{b9}, would have affected the {\it K--L\/} color
+\citet{b9}, would have affected the {\it K--L\/} colour
 significantly. AC Her, like other members of its class, is found
@@
 the diagram. \citet{b10} have already noticed that there are distinct
-differences between the {\it NIFT\/} colors of oxygen-rich and
+differences between the {\it NIFT\/} colours of oxygen-rich and
 carbon-rich objects. On the basis of an analysis, using a bigger
-sample of bright giant stars in the {\it NIFT\/} catalog, this has
-been interpreted by \citet{b25} as being due to a systematic
+sample of bright giant stars in the {\it NIFT\/} catalogue, this has
+been interpreted by as being due to a systematic
 difference in the dust grain emissivity index.
@@
 that none of the RV Tauri stars is found in the region of the
-two-color diagram occupied by the oxygen Miras indicates that the
+two-colour diagram occupied by the oxygen Miras indicates that the
 emissivity indices of the silicate grains in the two cases are
@@
 Table~\ref{t:sidetable} (except V Vul which has no available
-measurements) in the {\it J--K, K--L\/} plane. The colors, taken from
+measurements) in the {\it J--K, K--L\/} plane. The colours, taken from
 \citet{b9}, are averaged if more than one observation exists, because
@@
 \citet{b5} that variability has relatively little effect on
-colors. Barring RU Cen and AC Her, it is evident that stars belonging
+colours. Barring RU Cen and AC Her, it is evident that stars belonging
 to group B show systematically larger excebioms at {\it L\/} band for
@@
 for AC Her and RU Cen are consistent with the very low dust
-temperatures indicated by the far-infrared colors.
+temperatures indicated by the far-infrared colours.
 %
@@
 \citet{b4} has found that the two spectroscopic groups are well
-separated in the DDO color--color diagrams when mean colors are
+separated in the DDO colour--colour diagrams when mean colours are
 used for the individual objects. The clear separation of the
-spectroscopic subgroups A and B in the IR two-color diagram suggests
+spectroscopic subgroups A and B in the IR two-colour diagram suggests
 that the natures of dust grains in the envelopes in the two cases are
 not identical. This is to be expected because of the differences in
-the physical properties of the stars themselves. The average colors
+the physical properties of the stars themselves. The average colours
 of group B stars are bluer than group A, but the envelope dust
@@
 objects show systematically larger ({\it J--K\/}) and ({\it K--L\/})
-colors than RVa objects. Apparently, there is no distinction between
+colours than RVa objects. Apparently, there is no distinction between
 objects of the two light-curve types at far-infrared wavelengths
@@
 
-In the [12]--[25], [25]--[60] color diagram, RV Tauri stars populate
+In the [12]--[25], [25]--[60] colour diagram, RV Tauri stars populate
 cooler temperature regions $(T<600 \,\rmn{K})$, distinctly different from
@@
 reduced considerably during the recent past, contrary to the
-suggestion by \citet{b12}. In the two-color diagram, the
+suggestion by \citet{b12}. In the two-colour diagram, the
 blackbody line and the line corresponding to $\rho(r)\propto
@@
 
-\begin{thebibliography}{}
-\bibitem[\protect\citeauthoryear{Akash and Tirky}{1988}]{b24} 
-Akash, F. J. and Tirky, T. (1988). Proper multivariate conditional
-autoregressive models for spatial data analysis. {\it Biometrics} {\bf 196,} 173.
-
-\bibitem[\protect\citeauthoryear{Balaram et~al.}{1985a}]{b2} 
-Balaram, C. A., Neeraj, G., Haq, H. J., and Cliff, P. E., (1985a). {\it
-NIFT\/} 2nd edition. Boca Raton, Florida: Chapman and Hall.
-
-\bibitem[\protect\citeauthoryear{Commel}{1961}]{b18} 
-Commel, J. K. (1961). {\it National Sangget Academia}, 2nd edition.
-Hoboken, New Jersey: Wiley.
-
-\bibitem[\protect\citeauthoryear{Das  and Patra}{1986}]{b25} 
-Das, B. and Patra, H. M. (1986). Using counts to simultaneously estimate
-abundance and detection probabilities in a salamander community. {\it
-Herpetologica} {\bf 60,} 468--478.
-
-\bibitem[\protect\citeauthoryear{Emrat}{1974}]{b14} Emrat, T. (1974).
-{\it Topics in Stochastic Processes.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{Emrat}{1985}]{b15} Emrat, T. (1985).
-{\it Topics in Stochastic Processes.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{Goldman et~al.}{1987}]{b9} 
-Goldman, M. J. and Ewin, A. (1987). A comparison of smoothing
-techniques for CD4 data measured with error in a time-dependent Cox
-proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2061--2077.
-
-\bibitem[\protect\citeauthoryear{Goodsman}{1972}]{b8} 
-Goodsman, R. C. (1972). Testing hypotheses in the functional linear
-model. {\it Scandinavian Journal of Statistics} {\bf 30,} 241--251.
-
-\bibitem[\protect\citeauthoryear{Gooms}{1972}]{b5} Gooms, R. D.
-(1972). Goodsman, R.C. (1972). Testing hypotheses in the functional linear
-model. {\it Scandinavian Journal of Statistics} {\bf 31,} 315--323.
-
-\bibitem[\protect\citeauthoryear{Gooms  and Wool}{1970}]{b7} Gooms,
-R. D. and Wool, N. J. (1970). A comparison of smoothing
-techniques for CD4 data measured with errors in a time-dependent Cox
-proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2091--2099.
-
-\bibitem[\protect\citeauthoryear{Hackel}{1985}]{b10} 
-Hackel, P. (1985). {\it Topics in Stochastic Processes.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{\nobreak Holloman, \nobreak Tinku,  and Gerg}{Holloman et~al.}{1979}]{b11}
-Holloman, P. M., Tinku, H. A., and Gerg, I. (1979). A comparison of smoothing
-techniques for CD4 data measured with techniques a time-dependent Cox
-proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2105--2111.
-
-\bibitem[\protect\citeauthoryear{Juman}{1986}]{b12} 
-Juman, M. (1986). Using counts to simultaneously estimate
-abundance and detection probabilities in a salamander community. {\it
-Herpetologica} {\bf 61,} 482--495.
-
-\bibitem[\protect\citeauthoryear{Kartik B}{1969}]{b13} 
-Kartik, B. V. (1969). Using counts to simultaneously estimate
-abundance and detection probabilities in a salamander community. {\it
-Herpetologica} {\bf 62,} 511--519.
-
-\bibitem[\protect\citeauthoryear{Lenin}{1932}]{b17} 
-Lenin, D. B. (1932). A comparison of smoothing
-techniques for CD4 data measured with errors in a time-dependent Cox
-proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2125--2135.
-
-\bibitem[\protect\citeauthoryear{O'Rourke}{1979}]{b4} O'Rourke, D. (1996). Industrial ecology: A 
-critical review. {\it International Journal of Environment and Pollution}
-{\bf 6,} 389--112.
-
-\bibitem[\protect\citeauthoryear{Oman and \nobreak Raj}{1986}]{b19}
-Oman, F. M. and  Raj, E. (1986). {\it Topics in Stochastic Process.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{Prem et~al.}{1963}]{b20} Prem, G. W., Christ, W., Smap, J.,
-Wills, J. A. (1963). {\it Topics in Stochastic Processes.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{Rahul}{1981}]{b1} Rahul, S. R. (1981).
-Industrial ecology: A  critical review. {\it International Journal of
-Environment and Pollution} {\bf 6,} 371--375.
-
-\bibitem[\protect\citeauthoryear{Ram  and Shyam}{1972}]{b6} Ram, R. D.
-and Shyam, S. (1972). {\it Topics in Stochastic Process.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{Ravan  and Hari}{1983a}]{b21} Ravan,
-M. and Hari, S. (1983). Industrial ecology: A  critical review.
-{\it International Journal of Environment and Pollution} {\bf 6,} 389--395.
-
-\bibitem[\protect\citeauthoryear{Ravan  and Hari}{1983b}]{b22}
-Ravan, M. and Hari, S. (1984). Industrial ecology: A  critical
-review. {\it International Journal of Environment and Pollution} {\bf 7,} 512--519.
-
-\bibitem[\protect\citeauthoryear{Sharma et~al.}{1984}]{b16} Sharma,
-F. J. (1984). {\it Topics in Stochastic Process.} New York: Academic Press.
-
-\bibitem[\protect\citeauthoryear{Vim   and Potter}{1988}]{b23} Vim, W.
-E. and Potter, H. J. (1988). A  critical
-review. {\it International Journal of Environment and Pollution} {\bf 9,} 635--641.
-
-\end{thebibliography}
+\bibliographystyle{biom} \bibliography{biomsample.bib}
 
@@
 statistics and neglect all observational complications such as the
-line blending effect \citep[see][for example]{b11}. We concentrate here only on the
+line blending effect \citep[see][for example]{b11}.\vadjust{\vfill\pagebreak}
+ We concentrate here only on the
 statistics and neglect all observational complications such as the
-line blending effect \citep[see][for example]{b11}. \vadjust{\vfill\pagebreak}
+line blending effect \citep[see][for example]{b11}.
 

### 2012-07-31 paper/paper.tex
Paper style file

--- 2012-07-31 paper/example/biomsample.tex
@@
-% biomsample.tex
-%
-% v1.0 released 12th December 2006 (Dr. S. Sharma, Prof. N. Saxena, and Dr. S. Tahir)
-%
-% The biomsample.tex file has been amended to highlight
-% the proper use of LaTeX2e code with the class file
-% and using natbib cross-referencing.
-%
-\documentclass[useAMS,usenatbib]{biom}
-%\documentclass[useAMS,usenatbib,referee]{biom}
+%\documentclass[useAMS,usenatbib]{biom}
+\documentclass[useAMS,usenatbib,referee]{example/biom}
+
 %
@@
 %  using the referee option!!!!
-%
-%
-% If your system does not have the AMS fonts version 2.0 installed, then
-% remove the useAMS option.
-%
-% useAMS allows you to obtain upright Greek characters.
-% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
-% this guide for further information.
-%
-% If you are using AMS 2.0 fonts, bold math letters/symbols are available
-% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
-% preferably \bmath).
-%
-% The usenatbib command allows the use of Patrick Daly's natbib package for
-% cross-referencing.
-%
-% If you wish to typeset the paper in Times font (if you do not have the
-% PostScript Type 1 Computer Modern fonts you will need to do this to get
-% smoother fonts in a PDF file) then uncomment the next line
-% \usepackage{Times}
 
@@
 \usepackage[figuresright]{rotating}
-
+\graphicspath{{example/}{graphics/}}
 %% \raggedbottom % To avoid glue in typesetteing, sbs>>
@@
 
-\author{S. Sharma$^{*}$\email{email@address.com} \\
+\author{B. Calderhead$^{*}$\email{email@address.com} \\
 	   Institute of Physics, CA 560034, USA
 	   \and 
-	   A. Other$^{*}$\email{email1aa@address.com}\\
-	   Building, Institute, Street Address, City,
-	   Code, Country
+	   C. S. Gillespie$^{*}$\email{colin.gillespie@newcastle.ac.uk}\\
+	   School of Mathematics \& Statistics, Newcastle University,
+	   NE1 7RU, UK
 	   }
@@
 
-\date{{\it Received October} 2004. {\it Revised February} 2005.\newline 
-{\it Accepted March} 2005.}
+\date{}
 
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2006}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2012}
 
-\volume{59}
-\artmonth{December}
+\volume{XX}
+\artmonth{YYYY}
 \doi{10.1111/j.1541-0420.2005.00454.x}
@@
 \begin{keywords}
-Colostrum; Milk; Milk oligosaccharide; Non-human mammal.
+Stochastic; Moment-closure.
 \end{keywords}
@@
 
-It has been well established that RV Tauri variables pobiomss infrared
-emission far in excess of their expected blackbody continuum, arising
-from their extended cool dust envelopes \citep{b7,b5,b6}. Recently,
-\citep{b9} have given detailed descriptions of the near-infrared
-properties of RV Tauri stars. In this paper we present an analysis of
-the {\it NIFT\/} data of RV Tauri stars with the help of the
-far-infrared two-color diagram and a grid computed using a simple
-model of the dust envelope. Such two-color plots have already been
-employed extensively by several investigators to study the
-circumstellar envelopes around milk oligosaccharide and colostrum
-objects which are in the late stages of stellar evolution
-\citep{b10,b25,b24,b23}.
-
-Table~\ref{t:tableone} summarizes the basic data on the 17 objects
-detected at \hbox{60\,$\umu$m}. Apart from the {\it NIFT\/}
-identification and the flux densities at 12-, 25-, 60- and 100-$\umu$m
-wavebands, it gives the spectroscopic groups of \citet{b20}, the
-light-curve clabioms of \citet{b13} and the periods of light
-variation. The list, which contains about 20 per cent of all the known
-RV Tauri stars, is ebiomntially the same as that given by \citet{b12}.
-\begin{table*}
- \centering
- \def\~{\hphantom{0}}
- \begin{minipage}{175mm}
-  \caption{It is for us, the living, rather to be
-dedicated here to the unfinished work which, so nobly
-carried out}
-\label{t:tableone}
-  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{}}
-  \Hline
- & & \multicolumn{4}{c}{{Flux density (Jy)} \footnote{Observed by {\em NIFT}.}}\\ [1pt]
-\cline{3-7} \\ [-6pt]
-{Name}        &  & & & & & {Sp.} & \multicolumn{1}{r}{Period}& \multicolumn{1}{l}{Light-} 		\\ [-3pt]
-{Variable}\footnote{Observed by {\em NIFT}.}        &
-{\it NIFT} & {12$\,\umu$m} & {25$\,\umu$m} & {60$\,\umu$m}
-     & {100$\,\umu$m} &     {group} & \multicolumn{1}{r}{(d)}    &
-	 \multicolumn{1}{l}{curve type}& {\em T$_0$\,(\rm{K})}  \\ 
- \hline
- TW Cam & 04166$+$5719 & 8.27   & 5.62 & 1.82  & $<$1.73   & A & \~85.6 & a & 555 \\
- RV Tau & 04440$+$2605 & 22.53  & 18.08& 6.40  & 2.52      & A & \~78.9 & b & 460 \\
- DY Ori & 06034$+$1354 & 12.44  & 14.93& 4.12  & $<$11.22  & B & \~60.3 &  & 295 \\
- CT Ori & 06072$+$0953 & 6.16   & 5.57 & 1.22  & $<$1.54   & B & 135.6 &  & 330 \\
- SU Gem & 06108$+$2734 & 7.90   & 5.69 & 2.16  & $<$11.66  & A & \~50.1 & b & 575 \\
- UY CMa & 06160$-$1701 & 3.51   & 2.48 & 0.57  & $<$1.00   & B & 113.9 & a & 420 \\
- U Mon  & 07284$-$0940 & 124.30 & 88.43& 26.28 & 9.24      & A & \~92.3 & b & 480 \\
- AR Pup & 08011$-$3627 & 131.33 & 94.32& 25.81 & 11.65     & B & \~75.0 & b & 450 \\
- IW Car & 09256$-$6324 & 101/06 & 96.24& 34.19 & 13.07     & B & \~67.5 & b & 395 \\
- GK Car & 11118$-$5726 & 2.87   & 2.48 & 0.78  & $<$12.13  & B & \~55.6 &  & 405 \\
- RU Cen & 12067$-$4508 & 5.36   & 11.02& 5.57  & 2.01      & B & \~64.7 &  & 255 \\
- SX Cen & 12185$-$4856 & 5.95   & 3.62 & 1.09  & $<$1.50   & B & \~32.9 & b & 590 \\
- AI Sco & 17530$-$3348 & 17.68  & 11.46& 2.88  & $<$45.62  & A & \~71.0 & b & 480 \\
- AC Her & 18281$+$2149 & 41.47  & 65.33& 21.12 & 7.79      & B & \~75.5 & a & 260 \\
- R Sct  & 18448$-$0545 & 20.88  & 9.30 & 8.10  & $<$138.78 & A & 140.2 & a \\
- R Sge  & 20117$+$1634 & 10.63  & 7.57 & 2.10  & $<$1.66   & A & \~70.6 & b & 455 \\
- V Vul  & 20343$+$2625 & 12.39  & 5.72 & 1.29  & $<$6.96   & A & \~75.7 & a & 690\\
-\hline
-\end{tabular*}
-\end{minipage}
-\vspace*{-6pt}
-\end{table*}
-
 \section[]{Material Description of the Envelope\break Predominantly Model}
 
-If we assume that the dust grains in the envelope are  predominantly of
-the same kind and are in thermal  equilibrium,\vadjust{\pagebreak} the luminosity at
-frequency $\nu$ in the infrared is given by
-\begin{equation}
-   L(\nu)=\mskip-12mu\int\limits_{\rmn{envelope}}\mskip-12mu
-   \rho(r)Q_{\rmn{abs}}(\nu)B[\nu,T_{\rmn{g}}(r)]\exp [-\tau(\nu,r)]\>
-   \rmn{d}V,
-\label{eq:luminosity}
-\end{equation}
- where
- $Q_{\rmn{abs}}(\nu)$ is the absorption efficiency at frequency $\nu$,
- $\rho(r)$            is the dust grain density,
- $T_{\rmn{g}}(\nu)$    is the grain temperature,
- $B[\nu,T_{\rmn{g}}(r)]$  is the Planck function, and
- $\tau(\nu,r)$        is the optical depth at distance {\it r\/} from the
-                      center of the star.
-The temperature $T_{\rmn{g}}(r)$ is determined by the condition of energy
-balance: amount of energy radiated = amount of energy absorbed. The
-amount of energy absorbed at any point is proportional to the total
-available energy at that point, which consists of:\vspace*{-6pt}
-\begin{enumerate}
-  \item The attenuated and diluted stellar radiation. The attenuated and diluted stellar radiation;
-  \item Scattered radiation, and
-  \item Reradiation from other grains.
-\end{enumerate}
-
-The amount of energy absorbed at any point is proportional to the total
-available energy at that point
-\begin{itemize}
-  \item The attenuated and diluted stellar radiation. The attenuated and diluted stellar radiation;
-  \item Scattered radiation, and
-  \item Reradiation from other grains. Reradiation from other grains.
-\end{itemize}
-\begin{table}[b]
- \vspace*{-6pt}
- \centering
- \def\~{\hphantom{0}}
-  \caption{It is for us, the living, rather to be
-dedicated here to the unfinished work which, so nobly
-carried out}
-\label{t:tabletwo}
-  \begin{tabular*}{\columnwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{}}
-  \Hline
- & & \multicolumn{4}{c}{{Flux density (Jy)}}\\ [1pt]
-\cline{3-7} \\ [-6pt]
-{Name}        &  & & & & & {Sp.} \\ [-3pt]
-{Variable}        
-& {\it NIFT} & {12$\,\umu$m} & {25$\,\umu$m} & {60$\,\umu$m} & {100$\,\umu$m} &     {group} \\
- \hline
- TW Cam & 04166$+$5719 & 8.27   & 5.62 & 1.82  & $<$1.73   & A \\
- RV Tau & 04440$+$2605 & 22.53  & 18.08& 6.40  & 2.52      & A \\
- DY Ori & 06034$+$1354 & 12.44  & 14.93& 4.12  & $<$11.22  & B \\
- CT Ori & 06072$+$0953 & 6.16   & 5.57 & 1.22  & $<$1.54   & B \\
- SU Gem & 06108$+$2734 & 7.90   & 5.69 & 2.16  & $<$11.66  & A \\
- UY CMa & 06160$-$1701 & 3.51   & 2.48 & 0.57  & $<$1.00   & B \\
- U Mon  & 07284$-$0940 & 124.30 & 88.43& 26.28 & 9.24      & A \\
- AR Pup & 08011$-$3627 & 131.33 & 94.32& 25.81 & 11.65     & B \\
- IW Car & 09256$-$6324 & 101/06 & 96.24& 34.19 & 13.07     & B \\
- GK Car & 11118$-$5726 & 2.87   & 2.48 & 0.78  & $<$12.13  & B \\
- RU Cen & 12067$-$4508 & 5.36   & 11.02& 5.57  & 2.01      & B \\
- SX Cen & 12185$-$4856 & 5.95   & 3.62 & 1.09  & $<$1.50   & B \\
- AI Sco & 17530$-$3348 & 17.68  & 11.46& 2.88  & $<$45.62  & A \\
- AC Her & 18281$+$2149 & 41.47  & 65.33& 21.12 & 7.79      & B \\
- R Sct  & 18448$-$0545 & 20.88  & 9.30 & 8.10  & $<$138.78 & A \\
- R Sge  & 20117$+$1634 & 10.63  & 7.57 & 2.10  & $<$1.66   & A \\
- V Vul  & 20343$+$2625 & 12.39  & 5.72 & 1.29  & $<$6.96   & A \\
-\hline
-\end{tabular*}\vskip18pt
-\end{table}
-
-Detailed solutions of radiative transfer in circumstellar  dust
-shells by \citet{b21} indicate that the effect of heating by
-other grains becomes significant only at large optical depths at
-the absorbing frequencies $[\tau(\rmn{UV})\gg 10]$, and at optical
-depths $\tau(\rmn{UV})<1$ the grains have approximately the same
-temperature that they would have if they were seeing the starlight
-unattenuated and no other radiation.
-\begin{description}
-\item The Planck mean optical depths of circumstellar envelopes  around
-several RV Tauri stars. 
-\item The Planck mean optical depths of circumstellar envelopes  around
-several RV Tauri stars. 
-\item The Planck mean optical depths of circumstellar envelopes  around
-several RV Tauri stars. 
-\end{description}
-The pure terrestrial silicates
-or lunar silicates are found to be completely unsuitable to
-account for the infrared emission from circumstellar dust shells
-around M-type stars \citep{b21}. We assume that the absorption
-efficiency $Q_{\rmn{abs}} (\nu)$ in the infrared varies as
-$\nu^{\gamma}$. ${\gamma}=1$ appears to provide a reasonable fit
-in a variety of sources \citep*{b11,b12}. Under these
-circumstances the condition of energy balance implies that the
-dust temperature $T_{\rmn{g}}$ will vary as $r^{\beta}$.
-
-In view of the low value of the observed Planck mean  optical depth for
-the stellar radiation and the nature of the assumed frequency
-dependence of the absorption efficiency, the extinction of the infrared
-radiation by the dust envelope can be neglected; see Table~\ref{t:tabletwo}. If we consider the
-envelope to be spherically symmetric, (\ref{eq:luminosity}) reduces to
-\begin{equation}
-   L(\nu)=\!\!\int_{r_{1}}^{r_{2}}\!\!4\upi r^2\rho(r)\> Q_{\rmn{abs}}(\nu)B[\nu,T_{\rmn{g}}(r)]\> {\rmn{d}}r,
-\label{eq:reducelum}
-\end{equation}
-where $r_1$ and $r_2$ are the inner and
-outer radii of the shell. For a dusty density distribution
-$\rho(r)\propto r^{\alpha}$ and $r_2\gg r_1$, (\ref{eq:reducelum}) reduces to
-\begin{equation}
-   L(\nu)\propto \nu^{2+\gamma-Q}\int_{X_0}^{\infty}{{x^Q}\over
-   {\rmn{e}^x-1}}\rmn{d}x ,
-\label{eq:dusty}
-\end{equation}
-where, in (\ref{eq:dusty}), $Q=-(\alpha+\beta+3)/\beta$ and $X_0=(h\nu
-/kT_0)$. $T_0$ represents the temperature at the inner boundary of the
-dust shell where grains start condensing. In a steady radiation
-pressure driven mass outflow in the optically thin case, values of
-$\alpha$ lie near $-2$ \citep{b8}. $\gamma$ and $\beta$ are related by
-$\beta=-2/(\gamma+4)$.
-
-In the {\it NIFT\/} Point Source Catalog \citep[PSC;][]{b2}, the flux
-densities have been quoted at the effective wavelengths 12, 25, 60 and
-\hbox{100\,$\umu$m}, assuming a flat energy spectrum $[\nu F(\nu)=1]$
-for the observed sources. See Table~\ref{t:tablethree} for more
-details. For each model given by equation~\ref{eq:dusty}, using the relative
-system response, the color-correction factors in each of the {\it
-NIFT\/} passbands were calculated and the fluxes were converted into
-flux densities expected for a flat energy distribution, as assumed in
-the {\it NIFT\/} PSC, so that the computed colors can be directly
-compared with the colors determined from the catalog
-quantities. Such a procedure is more appropriate than correcting the
-{\it NIFT\/} colors for the energy distribution given by a particular
-model and then comparing them with those computed by the model.\vspace*{-6pt}
-
-\begin{table*}
- \centering
- \def\~{\hphantom{0}}
- \begin{minipage}{130mm}
-  \caption{It is for us, the living, rather to be
-dedicated here to the unfinished work which, so nobly
-carried out}
-\label{t:tablethree}
-  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{}}
-  \Hline
- & & \multicolumn{4}{c}{{Flux density (Jy)} \footnote{Observed by {\em NIFT}.}}\\ [1pt]
-\cline{3-7} \\ [-6pt]
-{Name}        &  & & & & & {Sp.} & \multicolumn{1}{r}{Period}& \multicolumn{1}{l}{Light-} 		\\ [-3pt]
-{Variable}\footnote{Observed by {\em NIFT}.}        &
-{\it NIFT} & {12$\,\umu$m} & {25$\,\umu$m} & {60$\,\umu$m}
-     & {100$\,\umu$m} &     {group} & \multicolumn{1}{r}{(d)}    &
-	 \multicolumn{1}{l}{curve type}& {\em T$_0$\,(\rm{K})}  \\ 
- \hline
- TW Cam & 04166$+$5719 & 8.27   & 5.62 & 1.82  & $<$1.73   & A & \~85.6 & a & 555 \\
- RV Tau & 04440$+$2605 & 22.53  & 18.08& 6.40  & 2.52      & A & \~78.9 & b & 460 \\
- DY Ori & 06034$+$1354 & 12.44  & 14.93& 4.12  & $<$11.22  & B & \~60.3 &  & 295 \\
- CT Ori & 06072$+$0953 & 6.16   & 5.57 & 1.22  & $<$1.54   & B & 135.6 &  & 330 \\
- SU Gem & 06108$+$2734 & 7.90   & 5.69 & 2.16  & $<$11.66  & A & \~50.1 & b & 575 \\
- UY CMa & 06160$-$1701 & 3.51   & 2.48 & 0.57  & $<$1.00   & B & 113.9 & a & 420 \\
- U Mon  & 07284$-$0940 & 124.30 & 88.43& 26.28 & 9.24      & A & \~92.3 & b & 480 \\
- AR Pup & 08011$-$3627 & 131.33 & 94.32& 25.81 & 11.65     & B & \~75.0 & b & 450 \\
- IW Car & 09256$-$6324 & 101/06 & 96.24& 34.19 & 13.07     & B & \~67.5 & b & 395 \\
- GK Car & 11118$-$5726 & 2.87   & 2.48 & 0.78  & $<$12.13  & B & \~55.6 &  & 405 \\
- RU Cen & 12067$-$4508 & 5.36   & 11.02& 5.57  & 2.01      & B & \~64.7 &  & 255 \\
- SX Cen & 12185$-$4856 & 5.95   & 3.62 & 1.09  & $<$1.50   & B & \~32.9 & b & 590 \\
- AI Sco & 17530$-$3348 & 17.68  & 11.46& 2.88  & $<$45.62  & A & \~71.0 & b & 480 \\
- AC Her & 18281$+$2149 & 41.47  & 65.33& 21.12 & 7.79      & B & \~75.5 & a & 260 \\
- R Sct  & 18448$-$0545 & 20.88  & 9.30 & 8.10  & $<$138.78 & A & 140.2 & a \\
- R Sge  & 20117$+$1634 & 10.63  & 7.57 & 2.10  & $<$1.66   & A & \~70.6 & b & 455 \\
- V Vul  & 20343$+$2625 & 12.39  & 5.72 & 1.29  & $<$6.96   & A & \~75.7 & a & 690\\
-\hline
-\end{tabular*}
-\end{minipage}
-\vspace*{-6pt}
-\end{table*}
-
-\section{An Example of Head One Color-Color Diagram An Example of Head One Color-Color Diagram}
-\subsection{An Example of Head Two: Color-Color Diagram An Example of Head Two: Color-Color Diagram}
-\label{ss:example}
-
-The IR color is defined as
-%\[
-\begin{eqnarray*}
-  [\nu_1]-[\nu_2]=-2.5\log [f(\nu_1)/f(\nu_2)],
-\end{eqnarray*}
-%\]
- where $\nu_1$ and $\nu_2$ are any two wavebands and $f(\nu_1)$ and
-$f(\nu_2)$ are the corresponding flux densities assuming a flat energy
-spectrum for the source. In Figure~\ref{f:mouse1column}, we have
-plotted the [25]--[60] colors of RV Tauri stars against their
-corresponding [12]--[25] colors derived from the {\it NIFT\/}
-data. Filled circles represent stars of group A and open circles stars
-of group B. \vspace*{6pt}
-\begin{longequation}
-\left(\begin{array}{cc}%
-[\tau_i(D-\alpha_iW]^{-1}+(\eta_0I+\eta_1W)[\tau_2(D-\alpha_2W)]^{-1}(\eta_0I+\eta_1W)&
-(\eta_0I+\eta_1W)[\tau_2(D-\alpha_2W)]^{-1}\\
-{[}\tau_2(D-\alpha_2W)]^{-1}(\eta_0I+\eta_1W)&[\tau_2(D-\alpha_2W)]^{-1}
-\end{array}
-\right).
-\label{eq:long} 
-\end{longequation}\vskip6pt 
-Equation~(\ref{eq:long}) is a long equation.  The two sets of
-near-parallel lines represent the loci of constant inner shell
-temperature $T_0$ and the quantity $Q$ defined above. The models
-correspond to the case of absorption efficiency $Q_{\rmn{abs}}(\nu)$
-varying as $\nu$ (with $\gamma=1$ and hence $\beta=-0.4$). We have
-omitted R Sct in Figure~\ref{f:mouse1column} because it shows a large
-deviation from the average relation shown by all the other objects. R
-Sct has a comparatively large excess at 60$\,\umu$m, but the extent of
-a possible contamination by the infrared cirrus \citep{b16} is
-unknown.  \citet{b9} found no evidence of the presence of a dust
-envelope at near-IR wavelengths and the spectrum was consistent with a
-stellar continuum. This explains why R Sct lies well below the mean
-relation shown by stars of groups A and C between the [3.6]--[11.3]
-color excess and the photometrically determined (Fe/H) \citep{b4}. R
-Sct has the longest period of 140$\,$d among the RV Tauri stars
-detected at far-infrared wavelengths and does the RV Tauri stars
-detected at far-infrared wavelengths and does the RV Tauri stars
-detected at far-infrared wavelengths and does not have the 10-$\umu$m
-emission feature seen in other objects \citep{b5,b19}. R Sct is
-probably the most irregular RV Tauri star known \citep{b17}.  In Web
-Appendix 1, we give a derivation that shows that this is to be
-expected.
-
-The inner shell temperatures $(T_0)$ derived for the various objects
-are also given in Table~\ref{t:tableone} and we find the majority
-of them to have temperatures in the narrow range
-400--600$\,$K. If the dependences of $Q_{\rmn{abs}}(\nu)$ on $\nu$ and
-$\rho(r)$ on $r$ are similar in all the objects considered, then in
-the color--color diagram they all should lie along a line
-corresponding to different values of $T_0$ and in
-Figure~\ref{f:bigmouse} we find that this is ebiomntially the case. In
-view of the quoted uncertainties in the flux measurements, we cannot
-attach much significance to the scatter in Figure~\ref{f:bigmouse}.
-
-\begin{figure}
- \centerline{\includegraphics[width=2.25in]{mouse.eps}}
-\caption{An example of figure caption. An example of figure
-caption. An example of figure caption. An example of figure
-caption.}
-\label{f:mouse1column}
-\end{figure}
-
-At \hbox{100\,$\umu$m} the infrared sky is characterized by emission,
-called infrared cirrus, from interstellar dust on all spatial scales
-\citep{b16}, thereby impairing the measurements at far-infrared
-wavelengths. \eqnbreaktop{3pc} In Figure~\ref{f:shortmouse}, we have plotted the
-[60]--[100] colors of the six RV Tauri stars detected at
-\hbox{100\,$\umu$m} against their [25]--[60] colors, along with the
-grid showing the regions of different values for inner shell
-temperature $T_0$ and the quantity $Q$, as in Figure~\ref{f:bigmouse}.
-The results indicated by Figure~\ref{f:shortmouse} are consistent with
-those derived from Figure~\ref{f:mouse1column}.  AR Pup shows a large
-excess at \hbox{100\,$\umu$m} but, in view of the large values for the
-cirrus flags given in the catalog, the intrinsic flux at
-\hbox{100\,$\umu$m} is uncertain.
-
 \subsection{Radial Distribution of Dust}
-
-From Figure~\ref{f:shortmouse}, it is evident that all RV Tauri stars
-lie between the lines corresponding to $Q=1.5$ and 0.5. With
- \[
-  \alpha=-(1+Q)\beta-3,
- \]
- these values suggest limits of $r^{-2.0}$ and $r^{-2.4}$ for the dust
-density variation, indicating a near-constant mass-loss rate.
-\citet{b12} has suggested that the density in the circumstellar
-envelope around RV Tauri stars varies as $r^{-1}$, implying a
-mass-loss rate that was greater in the past than it is currently.  By
-fitting a power law to the observed fluxes, such that $f(\nu)$ varies
-as $\nu^q$, values of $q$ determined by him for the various objects
-given in Table~\ref{t:tableone} lie in the range 0.6--1.2, with a mean
-$\skew5\bar q=0.98$. The assumption of a power law corresponds to the
-case of $X_0=0$ in equation (3) and hence we get
- \[
-  q=2+\gamma -Q.
- \]
-Since we assume that $Q_{\rmn{abs}}(\nu)$ varies as $\nu$, the
-resulting value for $Q$=2.0. None of the objects is found to lie in the
-corresponding region in the color--color diagram. Even this extreme
-value for $Q$ implies a density which varies as $r^{-1.8}$.
-
-\citet{b9} have reported that the simultaneous optical and near-IR
-data of AC Her can be fitted by a combination of two blackbodies
-at 5680 and 1800\,K, representing, respectively, the stellar and
-dust shell temperatures, and suggested that in RV Tauri stars the
-grain formation is a sporadic phenomenon and not a continuous
-process. Apparently, they have been influenced by the remark by
-\citet{b7} that their data in the 3.5--11$\,\umu$m region of AC
-Her indicated a dust temperature of $\sim$300\,K. We find that the
-{\it K--L\/} colors given by \citet{b5} and
-\citet{b9} are all consistent with each other. Surely, hot dust
-($\sim$1800\,K), if present at the time of observations by
-\citet{b9}, would have affected the {\it K--L\/} color
-significantly. AC Her, like other members of its class, is found
-to execute elongated loops in the ({\it U--B\/}), ({\it B--V\/})
-plane \citep{b20}, indicating that significant departure of the
-stellar continuum from the blackbody is to be expected. Further,
-their data show only a marginal excess at the near-IR wavelengths.\vspace*{-4pt}
-\begin{enumerate}
-\item[{\it Step} 1:] The attenuated and diluted stellar radiation;
-\item[{\it Step} 2:] Scattered radiation, and
-\item[{\it Step} 3:] Reradiation from other grains.\vspace*{-8pt}
-\end{enumerate}
-
-\enlargethispage{-2pt}
 
@@
 
-In Figure~\ref{f:shortmouse} we have also shown the positions of a
-sample of oxygen-rich and carbon-rich Miras.  We feel that the case
-for the existence of hot dust around AC Her and hence for the sporadic
-grain formation around RV Tauri stars is not strong. In
-Figure~\ref{f:bigmouse}, we find that AC Her and RU Cen lie very close
-to R Sct which, according to \citet{b9}, shows no evidence for the
-presence of a hot dust envelope. At the low temperatures
-characteristic of the Miras, a part of the emission at 12$\,\umu$m
-comes from the photosphere.  For a blackbody at 2000$\,$K, the ratio
-of fluxes at wavelengths of 12 and 2$\,\umu$m $(f_{12}/f_{2})\sim
-0.18$. The Miras shown in Figure~\ref{f:bigmouse} have
-$(f_{12}/f_{2})$ ratios larger than twice the above value. It is clear
-that the three groups of objects populate three different regions of
-the diagram. \citet{b10} have already noticed that there are distinct
-differences between the {\it NIFT\/} colors of oxygen-rich and
-carbon-rich objects. On the basis of an analysis, using a bigger
-sample of bright giant stars in the {\it NIFT\/} catalog, this has
-been interpreted by \citet{b25} as being due to a systematic
-difference in the dust grain emissivity index.
-
-\begin{figure*}
-  \centerline{\includegraphics[width=4.5in]{mouse.eps}}
-  \caption{An example of figure caption. An example of 
-  figure caption. An example of figure caption. An example of
-   figure caption. An example of figure caption.}
-\label{f:bigmouse}
-\end{figure*}
-
-\looseness-1U Mon shows the 10-$\umu$m silicate emission convincingly and, in
-most of the other objects for which low-resolution spectra in the
-near-infrared have been reported \citep{b5,b19}, the 10-$\umu$m
-emission may be partly attributed to silicates. Hence it is
-reasonable to expect that, in the envelopes around at least some
-of the RV Tauri stars, the dust grains are predominantly of
-silicates, as in the case of oxygen Miras \citep{b21}. The fact
-that none of the RV Tauri stars is found in the region of the
-two-color diagram occupied by the oxygen Miras indicates that the
-emissivity indices of the silicate grains in the two cases are
-different. Because of the higher temperatures and luminosities,
-the environment of grain formation will be different in RV Tauri
-stars.
-\begin{figure}[b]
-  \centerline{\includegraphics[width=2in]{mouse.eps}}
-  \caption{An example of short figure caption.}
-\vspace*{-3pt}
-\label{f:shortmouse}
-\end{figure}
-
-\paragraph{Correlation with subgroups}%
-\citet{b20} have identified three spectroscopic subgroups, which
-are designated as groups A, B and C. Objects of group A are
-metal-rich; group C are metal-poor; group B objects are also
-metal-poor, but  show carbon enhancements \citep{b20,b14,b4,b1}.\vspace*{-6pt}
-\begin{theorem}
-It is interesting to see that Table~\ref{t:tableone} contains no group
-C objects and that in Figure~\ref{f:shortmouse} there is a clear
-separation of the two spectroscopic subgroups A and B, with the
-demarcation occurring at an inner shell temperature of about 450$\,$K,
-group B stars having lower temperatures than group A.
-\end{theorem}
-\begin{proof}
-It is interesting to see that Table~\ref{t:tableone} contains no group
-C objects and that in Figure~\ref{f:shortmouse} there is a clear
-separation of the two spectroscopic subgroups A and B, with the
-demarcation occurring at an inner shell temperature of about 450$\,$K,
-group B stars having lower temperatures than group A.
-\end{proof}
-It is interesting to see that Table~\ref{t:tableone} contains no group
-C objects and that in Figure~\ref{f:shortmouse} there is a clear
-separation of the two spectroscopic subgroups A and B, with the
-demarcation occurring at an inner shell temperature of about 450$\,$K,
-group B stars having lower temperatures than group A. SX Cen is the
-only exception. \citet{b14} has reported that metal lines are stronger
-in SX Cen than in other group B objects. It may be worth noting that
-SX Cen has the shortest period among the 100 or so objects with the RV
-Tauri classification. RU Cen has the coolest inner shell temperature,
-as already suggested by the near-infrared spectrum\break \citep{b6}.
-
-\begin{sidewaystable}
- \centering
- \def\~{\hphantom{0}}
-% \begin{minipage}{225mm}
-  \hsize\textheight
-  \caption{It is for us, the living, rather to be
-dedicated here to the unfinished work which, so nobly
-carried out}
-\label{t:sidetable}
-\hskip-12pt\begin{tabular*}{\textheight}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}r@{\extracolsep{\fill}}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\extracolsep{\fill}}c@{\hskip12pt}}
-  \Hline
- & & \multicolumn{4}{c}{{Flux density (Jy)} \footnote{Observed by {\em NIFT}.}}\\ [1pt]
-\cline{3-7} \\ [-6pt]
-{Name}        &  & & & & & {Sp.} & \multicolumn{1}{r}{Period}& \multicolumn{1}{l}{Light-} 		\\ [-3pt]
-{Variable}\footnote{Observed by {\em NIFT}.}        &
-{\it NIFT} & {12$\,\umu$m} & {25$\,\umu$m} & {60$\,\umu$m}
-     & {100$\,\umu$m} &     {group} & \multicolumn{1}{r}{(d)}    &
-	 \multicolumn{1}{l}{curve type}& {\em T$_0$\,(\rm{K})}  \\ 
- \hline
- TW Cam & 04166$+$5719 & 8.27   & 5.62 & 1.82  & $<$1.73   & A & \~85.6 & a & 555 \\
- CT Ori & 06072$+$0953 & 6.16   & 5.57 & 1.22  & $<$1.54   & B & 135.6 &  & 330 \\
- SU Gem & 06108$+$2734 & 7.90   & 5.69 & 2.16  & $<$11.66  & A & \~50.1 & b & 575 \\
- UY CMa & 06160$-$1701 & 3.51   & 2.48 & 0.57  & $<$1.00   & B & 113.9 & a & 420 \\
- U Mon  & 07284$-$0940 & 124.30 & 88.43& 26.28 & 9.24      & A & \~92.3 & b & 480 \\
- AR Pup & 08011$-$3627 & 131.33 & 94.32& 25.81 & 11.65     & B & \~75.0 & b & 450 \\
- IW Car & 09256$-$6324 & 101/06 & 96.24& 34.19 & 13.07     & B & \~67.5 & b & 395 \\
- RU Cen & 12067$-$4508 & 5.36   & 11.02& 5.57  & 2.01      & B & \~64.7 &  & 255 \\
- SX Cen & 12185$-$4856 & 5.95   & 3.62 & 1.09  & $<$1.50   & B & \~32.9 & b & 590 \\
- AI Sco & 17530$-$3348 & 17.68  & 11.46& 2.88  & $<$45.62  & A & \~71.0 & b & 480 \\
- AC Her & 18281$+$2149 & 41.47  & 65.33& 21.12 & 7.79      & B & \~75.5 & a & 260 \\
- R Sct  & 18448$-$0545 & 20.88  & 9.30 & 8.10  & $<$138.78 & A & 140.2 & a \\
- R Sge  & 20117$+$1634 & 10.63  & 7.57 & 2.10  & $<$1.66   & A & \~70.6 & b & 455 \\
-\hline
-\end{tabular*}
-%\end{minipage}
-\end{sidewaystable}
-
-\subsubsection{Correlation with subgroups}%
-\paragraph{Head four correlation with subgroups}%
-Group B objects follow a different mean relationship from those of
-group A, having systematically larger 11-$\umu$m excess for a given
-excess at 3$\,\umu$m. For a general sample of RV Tauri stars, the
-distinction between the oxygen-rich and carbon-rich objects is not
-that apparent in the {\it JHKL\/} bands. In Figure~\ref{f:shortmouse}
-we have plotted the near-IR magnitudes of the objects given in
-Table~\ref{t:sidetable} (except V Vul which has no available
-measurements) in the {\it J--K, K--L\/} plane. The colors, taken from
-\citet{b9}, are averaged if more than one observation exists, because
-the internal agreements are found to be often of the order of
-observational uncertainties, in accordance with the earlier finding by
-\citet{b5} that variability has relatively little effect on
-colors. Barring RU Cen and AC Her, it is evident that stars belonging
-to group B show systematically larger excebioms at {\it L\/} band for
-a given excess at {\it K}. The low excebioms at near-IR wavelengths
-for AC Her and RU Cen are consistent with the very low dust
-temperatures indicated by the far-infrared colors.
-%
-
-It is already well established that from {\it UBV\/} photometry one
-can distinguish between groups A and B, members of group A being
-significantly redder than those of group B \citep{b20}.  Similarly,
-\citet{b4} has found that the two spectroscopic groups are well
-separated in the DDO color--color diagrams when mean colors are
-used for the individual objects. The clear separation of the
-spectroscopic subgroups A and B in the IR two-color diagram suggests
-that the natures of dust grains in the envelopes in the two cases are
-not identical. This is to be expected because of the differences in
-the physical properties of the stars themselves. The average colors
-of group B stars are bluer than group A, but the envelope dust
-temperatures of B are cooler than those of A. The near-IR spectra of
-AC Her and RU Cen are extremely similar \citep{b6}. The striking
-similarities in the optical spectra of AC Her and RU Cen have been
-pointed out by Bidelman \citep{b18}. We feel that the physical
-properties, including the chemical composition, of the grains formed
-in the circumstellar envelope strongly depend on those of the embedded
-star. This, probably, explains the diversity of the energy
-distributions of RV Tauri stars in the near-infrared found by
-\citet{b6}. On the basis of the observed differences in chemical
-abundances and space distribution of RV Tauri stars {\tt
-http://www.duke.edu/$\sim$delon001/Biometrics\_tables.pdf}.  See
-Section~\ref{s:discuss} for further discussion.
-
-\citet{b13} have subdivided RV Tauri stars into two clabioms, RVa and
-RVb, on the basis of their light curves; the former shows a constant
-mean brightness, whereas the latter shows a cyclically varying mean
-brightness. Extensive observations in the near-infrared show that, on
-average, RVb stars are redder than RVa stars, In RVb stars dust shells
-are denser in the inner regions and hence radiate strongly in the
-1--3$\,\umu$m region. Figure~\ref{f:shortmouse} confirms this; RVb
-objects show systematically larger ({\it J--K\/}) and ({\it K--L\/})
-colors than RVa objects. Apparently, there is no distinction between
-objects of the two light-curve types at far-infrared wavelengths
-(Figure~\ref{f:shortmouse}).
+% \begin{figure*}
+% %  \centerline{\includegraphics[width=4.5in]{mouse.eps}}
+%   \caption{An example of figure caption. An example of 
+%   figure caption. An example of figure caption. An example of
+%    figure caption. An example of figure caption.}
+% \label{f:bigmouse}
+% \end{figure*}
 
 \section{Discussion}
-\label{s:discuss}
-
-In the [12]--[25], [25]--[60] color diagram, RV Tauri stars populate
-cooler temperature regions $(T<600 \,\rmn{K})$, distinctly different from
-those occupied by the oxygen and carbon Miras. Using a simple model
-in which
-\begin{enumerate}
-  \item[1.] the envelope is spherically symmetric,
-  \item[2.] the IR-emitting grains are predominantly of the same kind, and
-  \item[3.] in the infrared the absorption efficiency $Q_{\rmn{abs}}
-        (\nu)\propto\nu$,
-\end{enumerate}
-we find that the {\it NIFT\/} fluxes are consistent with the
-density in the envelope $\rho(r)\propto r^{-2}$, where {\it r\/}
-is the radial distance. Such a dependence for the dust density
-implies that the mass-loss rates in RV Tauri stars have not
-reduced considerably during the recent past, contrary to the
-suggestion by \citet{b12}. In the two-color diagram, the
-blackbody line and the line corresponding to $\rho(r)\propto
-r^{-2.2}$ nearly overlap and the present data are insufficient to
-resolve between the two cases. The latter case is more physically
-reasonable, however.
 
@@
 
-\appendix
-
-\section{}
-\subsection{Computation of E$_i\{\alpha_i\}$}
-
-(This appendix was not part of the original paper by
-A.V.~Raveendran and is included here just for illustrative
-purposes. The references are not relevant to the text of the
-appendix, they are references from the bibliography used to
-illustrate text before and after citations.)
-
-Here is an equation; note how it is numbered:
-\begin{equation}
-A = B+C. 
-\label{eq:appeq}
-\end{equation}
-Equation~(\ref{eq:appeq}) is an the only numbered equation in this appendix.
-
-Spectroscopic observations of bright quasars show that the mean
-number density of Ly$\alpha$ forest lines, which satisfy certain
-criteria, evolves like $\rmn{d}N/\rmn{d}z=A(1+z)^\gamma$, where
-$A$ and~$\gamma$ are two constants.  Given the above intrinsic
-line distribution we examine the probability of finding large gaps
-in the Ly$\alpha$ forests.  We concentrate here only on the
-statistics and neglect all observational complications such as the
-line blending effect \citep[see][for example]{b11}. We concentrate here only on the
-statistics and neglect all observational complications such as the
-line blending effect \citep[see][for example]{b11}. We concentrate here only on the
-statistics and neglect all observational complications such as the
-line blending effect \citep[see][for example]{b11}.
-
-The references are not relevant to the text of the
-appendix, they are references from the bibliography used to
-illustrate text before and after citations.)
-
-Spectroscopic observations of bright quasars show that the mean
-number density of Ly$\alpha$ forest lines, which satisfy certain
-criteria, evolves like $\rmn{d}N/\rmn{d}z=A(1+z)^\gamma$, where
-$A$ and~$\gamma$ are two constants.  Given the above intrinsic
-line distribution we examine the probability of finding large gaps
-in the Ly$\alpha$ forests.  We concentrate here only on the
-statistics and neglect all observational complications such as the
-line blending effect \citep[see][for example]{b11}. We concentrate here only on the
-statistics and neglect all observational complications such as the
-line blending effect \citep[see][for example]{b11}. We concentrate here only on the
-statistics and neglect all observational complications such as the
-line blending effect \citep[see][for example]{b11}. \vadjust{\vfill\pagebreak}
-
-Suppose we have observed a Ly$\alpha$ forest between redshifts $z_1$
-and~$z_2$ and found $N-1$ lines.  For high-redshift quasars $z_2$~is
-usually the emission redshift $z_{\rmn{em}}$ and $z_1$ is set to
-$(\lambda_{\rmn{Ly}\beta}/\lambda_{\rmn{Ly}\alpha})(1+z_{\rmn{em}})=0.844
-(1+z_{\rmn{em}})$ to avoid contamination by Ly$\beta$ lines.  We
-want to know whether the largest gaps observed in the forest are
-significantly inconsistent with the above line distribution.  To do
-this we introduce a new variable~$x$:\vspace*{1.5pt}
-%
-\[
-x={(1+z)^{\gamma+1}-(1+z_1)^{\gamma+1} \over
-     (1+z_2)^{\gamma+1}-(1+z_1)^{\gamma+1}}.
-\]
-\vskip1.5pt%
-$x$ varies from 0 to 1.  We then have $\rmn{d}N/\rmn{d}x=\lambda$,
-where $\lambda$ is the mean number of lines between $z_1$ and $z_2$
-and is given by
-%
-\[%
-\lambda\equiv{A[(1+z_2)^{\gamma+1}-(1+z_1)^{\gamma+1}]\over\gamma+1}.
-\]
-%
-This means that the Ly$\alpha$ forest lines are uniformly
-distributed in~$x$.
-%
 \label{lastpage}

### 2012-08-02 paper/paper.tex
Added bullet points to the paper

@@
 
-\title[This is an Example of Recto Running Head]{This is an Example of
-an Article Title This is an Example of an Article Title}
+\title[Fast approximate proposals for exact inference in stochastic kinetic
+models]{Fast approximate proposals for exact inference in stochastic kinetic
+  models}
 
@@
 \begin{abstract}
-The world will little note, nor long remember, what we say here, but
-can never forget what they did here. It is for us, the living, rather
-to be dedicated here to the unfinished work which they have, thus far,
-so nobly carried out. It is rather for us to be here dedicated to the
-great task remaining before us--that from these honored dead we take
-increased devotion to that cause for which they here gave the last
-full measures of devotion--that we here highly resolve that these dead
-shall not have died in vain; that this nation shall have a new birth
-of freedom; and that this government of the people, by the people, for
-the people, shall not perish from the earth. The world will little
-note.
+\begin{itemize}
+\item Inference for MJP is difficult: non-linear likelihood, computational
+  expensive, proposals expensive, analytically intractable likelihood
+\item Data: Partially observed discrete, noisy time-course.
+\item Existing work for likelihood evaluations: 
+\begin{itemize}
+\item Likelihood calculations
+\begin{itemize}
+\item Exact: Boys et al, slow, not noise
+\item Approx SDE - Andy and Darren (with Noise)
+\item Approx MC - Andy and Colin (no noise)
+\item Approx LNA - Mark (no noise), Kolmo' (no noise, but check)
+\end{itemize}
+\item New:
+\begin{itemize}
+\item Approximate proposal mechanism based on the geometry of MC
+\begin{itemize}
+\item Overcome strong correlation structure which is standard with partially
+  observed data
+\item Fast proposals based on approximate geometry
+\item Accept/reject with approximate model before trying exact model
+\end{itemize}
+\item Inference is exact
+\item Including observational error
+\item Time course measurements, unlike Mark's LNA
+\end{itemize}
+\item Examples:
+\begin{itemize}
+\item Immigration-death model: exact proposal compared with approximate proposal
+  (no noise)
+\item Aphid model: 3 blocks * 3 water treats * 3 nitro treats with Poisson error
+\item Hidden states (counts), updated using standard method
+\end{itemize}
+\end{itemize}
+\end{itemize}
 \end{abstract}
@@
 
-\section[]{Material Description of the Envelope\break Predominantly Model}
+\begin{itemize}
+\item Inference for MJP is difficult: non-linear likelihood, computational
+  expensive, proposals expensive, analytically intractable likelihood
+\item Data: Partially observed discrete, noisy time-course.
+\item Existing work for likelihood evaluations: 
+\begin{itemize}
+\item Likelihood calculations
+\begin{itemize}
+\item Exact: Boys et al, slow, not noise
+\item Approx SDE - Andy and Darren (with Noise)
+\item Approx MC - Andy and Colin (no noise)
+\item Approx LNA - Mark (no noise), Kolmo' (no noise, but check)
+\end{itemize}
+\end{itemize}
+\item Novel stuff
+\end{itemize}
+Different from Mark's LNA paper:
+\begin{itemize}
+\item Analysis of impact of the approximate proposal scheme
+\item Using Noise
+\item Using delayed acceptance scheme so exact inference
+\item Time course data
+\item Using real data
+\end{itemize}
 
-\subsection{Radial Distribution of Dust}
+\section{Methods}
 
-\subsection{An Example of Head two}
-\subsubsection{An example of head three comparison with oxygen and~carbon~Miras}
+\subsection{Stochastic kinetic models}
 
-% \begin{figure*}
-% %  \centerline{\includegraphics[width=4.5in]{mouse.eps}}
-%   \caption{An example of figure caption. An example of 
-%   figure caption. An example of figure caption. An example of
-%    figure caption. An example of figure caption.}
-% \label{f:bigmouse}
-% \end{figure*}
+\subsection{Moment closure scheme}
+
+\subsection{Approximate Riemannian Geometry}
+
+\subsection{Delay acceptance scheme}
+
+Key point: little overhead for approximate likelihood
+
+\section{Example}
+
+\subsection{Immigration-death}
+
+\begin{itemize}
+\item Comparison between approximate proposal and true proposal
+\item Comparison between LNA and MC?
+\item Three examples: increase correlation
+\end{itemize}
+
+\subsection{Independent time course}
+
+Bimodal example??
+
+\subsection{Aphid simulation study}
+
+\section{Aphid real}
 
 \section{Discussion}
+
+\begin{itemize}
+\item Use of geometry vital in tackling real problems
+\item Could also use other approximation schemes such as the LNA??
+\end{itemize}
 

### 2012-08-02 Immigration-death/mcmc.R
More extreme immigration death likelihood

@@ -22,35 +22,11 @@ log_likelihood = function(k1, k2, t, x) {
     return(ll)
 }
 
-dd = read.csv("data/immigration_death.csv")
-log_likelihood(k1, k2, dd[,1], dd[,2])
+dd = read.csv("data/immigration_death1.csv")
+log_likelihood(1, 0.1, dd[,1], dd[,2])
 
-k1 = seq(0,3, 0.005)
-k2 = seq(0,0.4, 0.005)
+k1 = seq(log(0.001),log(10),  length.out=100)
+k2 = seq(log(0.001),log(10), length.out=100)
 d = outer(k1, k2, function(k1, k2) log_likelihood(k1, k2, dd[,1], dd[,2]))
-
-image(k1, k2, exp(d))
-# 
-# prop_theta = function(theta_cur){
-#     theta_cur
-# }
-# 
-# 
-# 
-# 
-# 
-# theta_cur = c(0.1, 0.1)
-# ll_cur = -Inf
-# for(i in 1:iters) {
-#     theta_prop  = prop_theta(theta_cur)
-#     ll_prop = log_likelihood(theta_prop)
-#     
-#     
-#     
-#     
-#     
-#     
-#     
-# }
-# 
-# 
+image(log(k1), log(k2), exp(d))
+points(1, 1,pch=18)

### 2012-08-02 Simulation/simulation.R

@@ -48,7 +48,7 @@ gillespie = function(IC, pars, maxtime=10) {
 }
 
 set.seed(1)
-dd = gillespie(c(0, 0), c(1, 0.1), 50)
+dd = gillespie(c(0, 0), c(1, 1), 50)
 dd_dis = discretise(dd, 5)
 
 ##Plot the data

### 2012-08-02 paper/paper.tex
Added to introduction.

@@
 
-\title[Fast approximate proposals for exact inference in stochastic kinetic
-models]{Fast approximate proposals for exact inference in stochastic kinetic
-  models}
+\title[Efficient inference using the approximate Riemannian geometry of stochastic population models]{Efficient inference using the approximate Riemannian geometry of stochastic population models}
 
-\author{B. Calderhead$^{*}$\email{email@address.com} \\
-	   Institute of Physics, CA 560034, USA
+\author{B. Calderhead$^{*}$\email{b.calderhead@ucl.ac.uk} \\
+	   Centre for Mathematics and Physics in the Life Sciences and Experimental Biology,\\University College London, UK
 	   \and 
@@
 \begin{itemize}
-\item Inference for MJP is difficult: non-linear likelihood, computational
+\item We present efficient and novel methodology for Bayesian inference over stochastic kinetic models with complex dynamics and large numbers of parameters.
+
+Inference for MJP is difficult: non-linear likelihood, computational
   expensive, proposals expensive, analytically intractable likelihood
@@
 
+Importance of stochastic population models for further scientific understanding of natural systems vs deterministic models.
+For example in ecology, where we often have to deal with discrete noisy data.
+Importance of parametric sensitivity has already been shown for determining vital properties of biological systems such as robustness and also in experimental design where the sensitivity gives information about the identifiability of individual rate constants.
+
+The sensitivity of parameters is also of central importance when inferring unknown parameter values for a mathematical model
+
+Performing exact inference over stochastic kinetic models described by Markov Jump Processes is extremely difficult.
+First and foremost, the likelihood is usually analytically intractable for models with levels of complexity suitable for describing natural phenomena.
+
+Approximations of the likelihood surface, such as LNA and moment closure.
+Parameter inference - want to explore the likelihood surface - can consider it as a Riemannian manifold.
+This manifold is an approximation of the true underlying Riemannian manifold of the analytically intractable likelihood.
+
+non-linear likelihood, computational expensive, proposals expensive, analytically intractable likelihood
+
 \section{Methods}
 
-\subsection{Stochastic kinetic models}
+\subsection{Stochastic Population Models}
 
-\subsection{Moment closure scheme}
+\subsection{Moment Closure Scheme}
 
@@
 
-\subsection{Delay acceptance scheme}
+\subsection{Delay Acceptance Scheme}
 

### 2012-08-02 paper/paper.tex
Added section headings

@@
 \end{itemize}
-\item Examples:
-\begin{itemize}
-\item Immigration-death model: exact proposal compared with approximate proposal
-  (no noise)
-\item Aphid model: 3 blocks * 3 water treats * 3 nitro treats with Poisson error
-\item Hidden states (counts), updated using standard method
-\end{itemize}
 \end{itemize}
@@
 
+C \& B
+
 \subsection{Moment Closure Scheme}
 
+CSG
+
 \subsection{Approximate Riemannian Geometry}
+BC
 
@@
 
+?
 Key point: little overhead for approximate likelihood
@@
 \begin{itemize}
-\item Comparison between approximate proposal and true proposal
-\item Comparison between LNA and MC?
-\item Three examples: increase correlation
+\item Comparison between Riemannian MC proposal, LNA proposal and true proposal
+\item Comparison between Riemannian and MH
+\item A single example, with highly correlated parameters
 \end{itemize}
 
-\subsection{Independent time course}
+\subsection{SIR (type) model}
 
-Bimodal example??
+\begin{itemize}
+\item Use model from Stumpf ABC paper (with real data?)
+\end{itemize}
 
-\subsection{Aphid simulation study}
+\subsection{Aphid data set}
 
-\section{Aphid real}
+\begin{itemize}
+\item 36 parameters - 18 birth, 18 death. 3 water treatments, 3 nitrogen treatments and 3 blocks, with interactions
+\item 5*27 (I think) latent data sets
+\item Exploit Sub-mannifolds for choosing parameter sets
+\item Poisson error structure
+\end{itemize}
 

### 2012-08-03 matlab_code/Imm_Death_mMALA_Simp_Full.m
Matlab code for immigration death model.

@@ -1,0 +1,280 @@
+function [ ] = Imm_Death_mMALA_Simp_Full( y, Time, k1, k2 )
+
+warning off
+
+% Random Numbers...
+randn('state', sum(100*clock));
+rand('twister', sum(100*clock));
+
+[N,D] = size(y);
+D = 2;
+        
+TimeStep = diff(Time);
+
+% Langevin Setup
+NumOfIterations = 10000;
+BurnIn          = 5000;
+StepSize        = 0.05;
+                
+
+Proposed = 0;
+Accepted = 0;
+
+
+% Set initial values of w
+Paras  = [k1 k2];
+ParasSaved = zeros(NumOfIterations-BurnIn,D);
+
+% Calculate joint log likelihood for current w
+%LogPrior      = LogNormPDF(zeros(1,D),Paras,alpha);
+
+Mu  = Calc_Mean(k1,k2,y(1:N-1),TimeStep);
+Var = Calc_Variance(k1,k2,y(1:N-1),TimeStep);
+%LogLikelihood  = sum( log( normpdf(y(2:end),Mu,sqrt(Var)) ) );
+LogLikelihood = pn(k1, k2, TimeStep, y);
+
+CurrentLJL    = LogLikelihood; % + LogPrior;
+
+
+%%% Pre-Calculations %%%
+ParasNew = Paras;
+
+% Calculate G based on new parameters
+% Calculate metric tensor
+dM_dk1     = dMean_dk1(k1,k2,y(1:N-1),TimeStep);
+dSigma_dk1 = dVariance_dk1(k1,k2,y(1:N-1),TimeStep);
+dSigma_dk1 = diag(dSigma_dk1);
+
+dM_dk2     = dMean_dk2(k1,k2,y(1:N-1),TimeStep);
+dSigma_dk2 = dVariance_dk2(k1,k2,y(1:N-1),TimeStep);
+dSigma_dk2 = diag(dSigma_dk2);
+
+Sigma     = diag(Var);
+InvSigma  = inv(Sigma);
+dInvSigma_dk1 = -InvSigma*dSigma_dk1*InvSigma;
+dInvSigma_dk2 = -InvSigma*dSigma_dk2*InvSigma;
+
+L_deriv(1) = (dM_dk1'*InvSigma)*(y(2:end) - Mu) - 0.5*((y(2:end) - Mu)'*dInvSigma_dk1*(y(2:end) - Mu)) - 0.5*trace(InvSigma*dSigma_dk1);
[…]

### 2012-08-03 paper/paper.tex
Added timescales

@@
 \begin{abstract}
-\begin{itemize}
-\item We present efficient and novel methodology for Bayesian inference over stochastic kinetic models with complex dynamics and large numbers of parameters.
-
-Inference for MJP is difficult: non-linear likelihood, computational
-  expensive, proposals expensive, analytically intractable likelihood
-\item Data: Partially observed discrete, noisy time-course.
-\item Existing work for likelihood evaluations: 
-\begin{itemize}
-\item Likelihood calculations
-\begin{itemize}
-\item Exact: Boys et al, slow, not noise
-\item Approx SDE - Andy and Darren (with Noise)
-\item Approx MC - Andy and Colin (no noise)
-\item Approx LNA - Mark (no noise), Kolmo' (no noise, but check)
-\end{itemize}
-\item New:
-\begin{itemize}
-\item Approximate proposal mechanism based on the geometry of MC
-\begin{itemize}
-\item Overcome strong correlation structure which is standard with partially
-  observed data
-\item Fast proposals based on approximate geometry
-\item Accept/reject with approximate model before trying exact model
-\end{itemize}
-\item Inference is exact
-\item Including observational error
-\item Time course measurements, unlike Mark's LNA
-\end{itemize}
-\end{itemize}
-\end{itemize}
+Abstract
 \end{abstract}
@@
 
+\section{Useful Papers}
+
+\begin{itemize}
+\item Papers cited in \textbf{refs.bib}
+\item Useful papers put in papers directory
+\end{itemize}
+
 \section{Introduction}
-\label{s:intro}
+\label{s:intro}\textbf{31/8: BC/CSG}
 
@@
   \begin{itemize}
-\item Comparison between Riemannian MC proposal, LNA proposal and true proposal
-\item Comparison between Riemannian and MH
-\item A single example, with highly correlated parameters
+  \item Calculate exact proposal for comparison (\textbf{17/8: CSG})
+  \item Construct LNA model for ID (\textbf{14/9: CSG/BC})
+  \item Graphs:
+    \begin{itemize}
+    \item Data: \textbf{17/8: CSG}
+    \item Geometry proposal: 3 proposals for the 3 derviates: k1\^2, k1k2, k2\^2
+      \textbf{24/8: }
+    \item Likelihood: Exact likelihood vs LNA vs MC \textbf{24/8: }
+    \item Delay acceptance(?)
+    \item Sampling efficiences M-H vs RM (appendix)
+    \end{itemize}
   \end{itemize}
@@
     \begin{itemize}
-\item Use model from Stumpf ABC paper (with real data?)
+    \item Construct moment equations (\textbf{17/8: CSG}) Lognormal?
+    \item Construct proposal
+    \item Delay acceptance
+    \item Run experiments
+    \item Graphs:
+      \begin{itemize}
+      \item Data
+      \item Sampling efficiences M-H vs RM (appendix)
+      \item Posterior compare to Stumpf
+      \end{itemize}
     \end{itemize}
@@
 
+\subsubsection{Introduction}
+
+36 parameters - 18 birth, 18 death. 3 water treatments, 3 nitrogen treatments
+and 3 blocks, with interactions. 5*27 (I think) latent data sets. Exploit Sub-mannifolds for choosing parameter sets
+Poisson error structure.
+
     \begin{itemize}
-\item 36 parameters - 18 birth, 18 death. 3 water treatments, 3 nitrogen treatments and 3 blocks, with interactions
-\item 5*27 (I think) latent data sets
-\item Exploit Sub-mannifolds for choosing parameter sets
-\item Poisson error structure
+    \item Construct moment equations (appendix) \textbf{Done}
+    \item Construct proposal (appendix)
+    \item Delay acceptance
+    \item Run experiments
+    \item Graphs:
+      \begin{itemize}
+      \item Data \textbf{Done}
+      \item Sampling efficiences M-H vs RM; ESS
+      \item Posteriors
+      \end{itemize}
     \end{itemize}

### 2012-08-03 Immigration-death/mcmc.R
Minor changes

@@ -22,11 +22,11 @@ log_likelihood = function(k1, k2, t, x) {
     return(ll)
 }
 
-dd = read.csv("data/immigration_death1.csv")
+dd = read.csv("data/immigration_death_k1_1_k2_1.csv")
 log_likelihood(1, 0.1, dd[,1], dd[,2])
 
-k1 = seq(log(0.001),log(10),  length.out=100)
-k2 = seq(log(0.001),log(10), length.out=100)
+k1 = seq(log10(1.1),log10(100),  length.out=500)
+k2 = seq(log10(1.1),log10(100), length.out=500)
 d = outer(k1, k2, function(k1, k2) log_likelihood(k1, k2, dd[,1], dd[,2]))
-image(log(k1), log(k2), exp(d))
+image(log10(k1), log10(k2), exp(d))
 points(1, 1,pch=18)

### 2012-08-03 Immigration-death/tensor_calculation.R

@@ -35,6 +35,52 @@ d1V_dk2 = function(k1, k2, n0, t){
     v = V(k1, k2, n0, tau)
     -1/v*dV_dk2(k1,k2,n0,tau)/v
 }
+#########################################################
+
+
+##k1 = immigration rate, k2 =death
+E = function(k1, k2, n0, t) {
+    (k1 - k2*n0)*t
+}
+
+V = function(k1, k2, n0, t) {
+    (k1 + k2*n0)*t
+}
+
+##First-order 
+dE_dk1 = function(k1, k2,n0, t) {
+    t
+}
+
+dE_dk2 = function(k1, k2,n0, t) {
+    n0*t
+}
+
+##Derivative of Variance wrt to theta
+dV_dk1 = function(k1, k2,n0, t) {
+    t
+}
+dV_dk2 = function(k1, k2,n0, t) {
+    n0*t
+}
+
+##Derivative of 1/Variance wrt to theta
+d1V_dk1 = function(k1, k2, n0, t){
+    v = V(k1,k2,n0,tau)
+    -1/v*dV_dk1(k1,k2,n0,tau)/v
+}
+
+d1V_dk2 = function(k1, k2, n0, t){
+    v = V(k1, k2, n0, tau)
+    -1/v*dV_dk2(k1,k2,n0,tau)/v
+}
+
+
+
+
+
+
+
 
 ##Work out Ll
 L = function(k1, k2, t, x) {
@@ -168,14 +214,38 @@ L_deriv2 = function(k1, k2, t, x) {
 }
     
 
-dd = read.csv("data/immigration_death.csv")
+dd = read.csv("data/immigration_death1.csv")
 k1 = 1; k2 = 0.1
 L(k1, k2, dd$times, dd$n)
 L_deriv(k1, k2, dd$times, dd$n)
 L_deriv2(k1, k2, dd$times, dd$n)
 
+L_deriv2_k1k1()
+
+1/100
+(1.3-0.07)/20
+
+#k1 = seq(0.5,1.5, length.out=100)
+k1 = seq(0.5, 1.5, 0.05)
+k2 = seq(0.07, 1.3, 0.0615)
+d11 = outer(k1, k2, function(k1, k2) L_deriv2_k1k1(k1, k2, dd[,1], dd[,2]))
[…]

### 2012-08-07 paper/paper.tex
Moved to PNAS style file

@@
-%\documentclass[useAMS,usenatbib]{biom}
-\documentclass[useAMS,usenatbib,referee]{example/biom}
+%% PNAStmpl.tex
+%% Template file to use for PNAS articles prepared in LaTeX
+%% Version: Apr 14, 2008
 
-%
-%
-%  Papers submitted to Biometrics should ALWAYS be prepared
-%  using the referee option!!!!
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% BASIC CLASS FILE 
+%% PNAStwo for two column articles is called by default.
+%% Uncomment PNASone for single column articles. One column class
+%% and style files are available upon request from pnas@nas.edu.
+%% (uncomment means get rid of the '%' in front of the command)
 
-%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
+%\documentclass{pnasone}
+\documentclass{pnastwo}
 
-\def\bSig\mathbf{\Sigma}
-\newcommand{\VS}{V\&S}
-\newcommand{\tr}{\mbox{tr}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Changing position of text on physical page:
+%% Since not all printers position
+%% the printed page in the same place on the physical page,
+%% you can change the position yourself here, if you need to:
 
-%  If you have a landscape table you need to use the rotating package
+% \advance\voffset -.5in % Minus dimension will raise the printed page on the 
+                         %  physical page; positive dimension will lower it.
 
-\usepackage[figuresright]{rotating}
-\graphicspath{{example/}{graphics/}}
-%% \raggedbottom % To avoid glue in typesetteing, sbs>>
+%% You may set the dimension to the size that you need.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% OPTIONAL GRAPHICS STYLE FILE
 
-\setcounter{footnote}{2}
+%% Requires graphics style file (graphicx.sty), used for inserting
+%% .eps files into LaTeX articles.
+%% Note that inclusion of .eps files is for your reference only;
+%% when submitting to PNAS please submit figures separately.
 
-\title[Efficient inference using the approximate Riemannian geometry of stochastic population models]{Efficient inference using the approximate Riemannian geometry of stochastic population models}
+%% Type into the square brackets the name of the driver program 
+%% that you are using. If you don't know, try dvips, which is the
+%% most common PC driver, or textures for the Mac. These are the options:
 
-\author{B. Calderhead$^{*}$\email{b.calderhead@ucl.ac.uk} \\
-	   Centre for Mathematics and Physics in the Life Sciences and Experimental Biology,\\University College London, UK
-	   \and 
-	   C. S. Gillespie$^{*}$\email{colin.gillespie@newcastle.ac.uk}\\
-	   School of Mathematics \& Statistics, Newcastle University,
-	   NE1 7RU, UK
-	   }
+% [dvips], [xdvi], [dvipdf], [dvipdfm], [dvipdfmx], [pdftex], [dvipsone],
+% [dviwindo], [emtex], [dviwin], [pctexps], [pctexwin], [pctexhp], [pctex32],
+% [truetex], [tcidvi], [vtex], [oztex], [textures], [xetex]
+
+%\usepackage[dvips]{graphicx}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% OPTIONAL POSTSCRIPT FONT FILES
+
+%% PostScript font files: You may need to edit the PNASoneF.sty
+%% or PNAStwoF.sty file to make the font names match those on your system. 
+%% Alternatively, you can leave the font style file commands commented out
+%% and typeset your article using the default Computer Modern 
+%% fonts (recommended). If accepted, your article will be typeset
+%% at PNAS using PostScript fonts.
+
+% Choose PNASoneF for one column; PNAStwoF for two column:
+%\usepackage{PNASoneF}
+%\usepackage{PNAStwoF}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% ADDITIONAL OPTIONAL STYLE FILES
+
+%% The AMS math files are commonly used to gain access to useful features
+%% like extended math fonts and math commands.
+
+\usepackage{amssymb,amsfonts,amsmath}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% OPTIONAL MACRO FILES
+%% Insert self-defined macros here.
+%% \newcommand definitions are recommended; \def definitions are supported
+
+%\newcommand{\mfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}}
+%\def\s{\sigma}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Don't type in anything in the following section:
+%%%%%%%%%%%%
+%% For PNAS Only:
+\contributor{Submitted to Proceedings
+of the National Academy of Sciences of the United States of America}
+\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
+\copyrightyear{2008}
+\issuedate{Issue Date}
+\volume{Volume}
+\issuenumber{Issue Number}
+%%%%%%%%%%%%
 
@@
 
-\date{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2012}
+%% For titles, only capitalize the first letter
+%% \title{Almost sharp fronts for the surface quasi-geostrophic equation}
 
-\volume{XX}
-\artmonth{YYYY}
-\doi{10.1111/j.1541-0420.2005.00454.x}
+\title{Efficient inference using the approximate Riemannian geometry of stochastic population models}
 
-%  This label and the label ``lastpage'' are used by the \pagerange
-%  command above to give the page range for the article
+%% Enter authors via the \author command.  
+%% Use \affil to define affiliations.
+%% (Leave no spaces between author name and \affil command)
 
-\label{firstpage}
+%% Note that the \thanks{} command has been disabled in favor of
+%% a generic, reserved space for PNAS publication footnotes.
 
-%  pub the summary here
+%% \author{<author name>
+%% \affil{<number>}{<Institution>}} One number for each institution.
+%% The same number should be used for authors that
+%% are affiliated with the same institution, after the first time
+%% only the number is needed, ie, \affil{number}{text}, \affil{number}{}
+%% Then, before last author ...
+%% \and
+%% \author{<author name>
+%% \affil{<number>}{}}
 
-\begin{abstract}
-Abstract
-\end{abstract}
+%% For example, assuming Garcia and Sonnery are both affiliated with
+%% Universidad de Murcia:
+%% \author{Roberta Graff\affil{1}{University of Cambridge, Cambridge,
+%% United Kingdom},
+%% Javier de Ruiz Garcia\affil{2}{Universidad de Murcia, Bioquimica y Biologia
+%% Molecular, Murcia, Spain}, \and Franklin Sonnery\affil{2}{}}
 
-%
-%  Please place your key words in alphabetical order, separated
-%  by semicolons, with the first letter of the first word capitalized,
-%  and a period at the end of the list.
-%
+\author{B. Calderhead\affil{1}{UCL}, C. S. Gillespie\affil{2}{NCL}}
+% \email{b.calderhead@ucl.ac.uk}
+% \email{colin.gillespie@newcastle.ac.uk}
+% \\
+% 	   Centre for Mathematics and Physics in the Life Sciences and Experimental Biology,\\University College London, UK
+% 	   \and 
+% 	   School of Mathematics \& Statistics, Newcastle University,
+% 	   NE1 7RU, UK
+\contributor{Submitted to Proceedings of the National Academy of Sciences
+of the United States of America}
 
-\begin{keywords}
-Stochastic; Moment-closure.
-\end{keywords}
+%% The \maketitle command is necessary to build the title page.
+\maketitle
 
-\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{article}
+
+\begin{abstract} -- enter abstract text here -- \end{abstract}
+
+%% When adding keywords, separate each term with a straight line: |
+\keywords{term | term | term}
+
+%% Optional for entering abbreviations, separate the abbreviation from
+%% its definition with a comma, separate each pair with a semicolon:
+%% for example:
+%% \abbreviations{SAM, self-assembled monolayer; OTS,
+%% octadecyltrichlorosilane}
+
+% \abbreviations{}
+
+%% The first letter of the article should be drop cap: \dropcap{}
+%\dropcap{I}n this article we study the evolution of ''almost-sharp'' fronts
+
+%% Enter the text of your article beginning here and ending before
+%% \begin{acknowledgements}
+%% Section head commands for your reference:
+%% \section{}
+%% \subsection{}
+%% \subsubsection{}
 
@@
 
-\backmatter
+%% == end of paper:
 
-%%%%%% include this section if you wish to acknowledge people,
-%%%%%% grant support, etc.
+%% Optional Materials and Methods Section
+%% The Materials and Methods section header will be added automatically.
 
-\section*{Acknowledgements}
+%% Enter any subheads and the Materials and Methods text below.
+%\begin{materials}
+% Materials text
+%\end{materials}
 
-The authors thank Professor A. Sen for some helpful suggestions,
-Dr C. R. Rangarajan for a critical reading of the original version of the
-paper, and an anonymous referee for very useful comments that improved
-the presentation of the paper.\vspace*{-8pt}
+%% Optional Appendix or Appendices
+%% \appendix Appendix text...
+%% or, for appendix with title, use square brackets:
+%% \appendix[Appendix Title]
 
-%%%%%% include this section only if your manuscript refers to supplementary
-%%%%%% materials -- see Instructions for Authors at 
-%%%%%% http://www.tibs.org/biometrics
+\begin{acknowledgments}
+Thanks to AG and Ohio state University
+\end{acknowledgments}
 
-\section*{Supplementary Materials}
+%% PNAS does not support submission of supporting .tex files such as BibTeX.
+%% Instead all references must be included in the article .tex document. 
+%% If you currently use BibTeX, your bibliography is formed because the 
+%% command \verb+\bibliography{}+ brings the <filename>.bbl file into your
+%% .tex document. To conform to PNAS requirements, copy the reference listings
+%% from your .bbl file and add them to the article .tex file, using the
+%% bibliography environment described above.
 
-Web Appendix 1 referenced in Section~\ref{ss:example} is available
-with this paper at the Biometrics website on Wiley Online Library.
-\vspace*{-8pt}
+%%  Contact pnas@nas.edu if you need assistance with your
+%%  bibliography.
 
-\begin{thebibliography}{}
-\bibitem[\protect\citeauthoryear{Akash and Tirky}{1988}]{b24} 
-Akash, F. J. and Tirky, T. (1988). Proper multivariate conditional
-autoregressive models for spatial data analysis. {\it Biometrics} {\bf 196,} 173.
+% Sample bibliography item in PNAS format:
+%% \bibitem{in-text reference} comma-separated author names up to 5,
+%% for more than 5 authors use first author last name et al. (year published)
+%% article title  {\it Journal Name} volume #: start page-end page.
+%% ie,
+% \bibitem{Neuhaus} Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) 
+% A short C-terminal sequence is necessary and sufficient for the
+% targeting of chitinases to the plant vacuole. 
+% {\it Proc Natl Acad Sci USA} 88:10362-10366.
 
-\bibitem[\protect\citeauthoryear{Balaram et~al.}{1985a}]{b2} 
-Balaram, C. A., Neeraj, G., Haq, H. J., and Cliff, P. E., (1985a). {\it
-NIFT\/} 2nd edition. Boca Raton, Florida: Chapman and Hall.
+%% Enter the largest bibliography number in the facing curly brackets
+%% following \begin{thebibliography}
 
-\bibitem[\protect\citeauthoryear{Commel}{1961}]{b18} 
-Commel, J. K. (1961). {\it National Sangget Academia}, 2nd edition.
-Hoboken, New Jersey: Wiley.
+% \begin{thebibliography}{}
+% 
+% \end{thebibliography}
 
-\bibitem[\protect\citeauthoryear{Das  and Patra}{1986}]{b25} 
-Das, B. and Patra, H. M. (1986). Using counts to simultaneously estimate
-abundance and detection probabilities in a salamander community. {\it
-Herpetologica} {\bf 60,} 468--478.
+\end{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\bibitem[\protect\citeauthoryear{Emrat}{1974}]{b14} Emrat, T. (1974).
-{\it Topics in Stochastic Processes.} New York: Academic  Press.
+%% Adding Figure and Table References
+%% Be sure to add figures and tables after \end{article}
+%% and before \end{document}
 
-\bibitem[\protect\citeauthoryear{Emrat}{1985}]{b15} Emrat, T. (1985).
-{\it Topics in Stochastic Processes.} New York: Academic  Press.
+%% For figures, put the caption below the illustration.
+%%
+%% \begin{figure}
+%% \caption{Almost Sharp Front}\label{afoto}
+%% \end{figure}
 
-\bibitem[\protect\citeauthoryear{Goldman et~al.}{1987}]{b9} 
-Goldman, M. J. and Ewin, A. (1987). A comparison of smoothing
-techniques for CD4 data measured with error in a time-dependent Cox
-proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2061--2077.
+%% For Tables, put caption above table
+%%
+%% Table caption should start with a capital letter, continue with lower case
+%% and not have a period at the end
+%% Using @{\vrule height ?? depth ?? width0pt} in the tabular preamble will
+%% keep that much space between every line in the table.
 
-\bibitem[\protect\citeauthoryear{Goodsman}{1972}]{b8} 
-Goodsman, R. C. (1972). Testing hypotheses in the functional linear
-model. {\it Scandinavian Journal of Statistics} {\bf 30,} 241--251.
+%% \begin{table}
+%% \caption{Repeat length of longer allele by age of onset class}
+%% \begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
+%% table text
+%% \end{tabular}
+%% \end{table}
 
-\bibitem[\protect\citeauthoryear{Gooms}{1972}]{b5} Gooms, R. D.
-(1972). Goodsman, R.C. (1972). Testing hypotheses in the functional linear
-model. {\it Scandinavian Journal of Statistics} {\bf 31,} 315--323.
+%% For two column figures and tables, use the following:
 
-\bibitem[\protect\citeauthoryear{Gooms  and Wool}{1970}]{b7} Gooms,
-R. D. and Wool, N. J. (1970). A comparison of smoothing
-techniques for CD4 data measured with errors in a time-dependent Cox
-proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2091--2099.
+%% \begin{figure*}
+%% \caption{Almost Sharp Front}\label{afoto}
+%% \end{figure*}
 
-\bibitem[\protect\citeauthoryear{Hackel}{1985}]{b10} 
-Hackel, P. (1985). {\it Topics in Stochastic Processes.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{\nobreak Holloman, \nobreak Tinku,  and Gerg}{Holloman et~al.}{1979}]{b11}
-Holloman, P. M., Tinku, H. A., and Gerg, I. (1979). A comparison of smoothing
-techniques for CD4 data measured with techniques a time-dependent Cox
-proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2105--2111.
-
-\bibitem[\protect\citeauthoryear{Juman}{1986}]{b12} 
-Juman, M. (1986). Using counts to simultaneously estimate
-abundance and detection probabilities in a salamander community. {\it
-Herpetologica} {\bf 61,} 482--495.
-
-\bibitem[\protect\citeauthoryear{Kartik B}{1969}]{b13} 
-Kartik, B. V. (1969). Using counts to simultaneously estimate
-abundance and detection probabilities in a salamander community. {\it
-Herpetologica} {\bf 62,} 511--519.
-
-\bibitem[\protect\citeauthoryear{Lenin}{1932}]{b17} 
-Lenin, D. B. (1932). A comparison of smoothing
-techniques for CD4 data measured with errors in a time-dependent Cox
-proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2125--2135.
-
-\bibitem[\protect\citeauthoryear{O'Rourke}{1979}]{b4} O'Rourke, D. (1996). Industrial ecology: A 
-critical review. {\it International Journal of Environment and Pollution}
-{\bf 6,} 389--112.
-
-\bibitem[\protect\citeauthoryear{Oman and \nobreak Raj}{1986}]{b19}
-Oman, F. M. and  Raj, E. (1986). {\it Topics in Stochastic Process.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{Prem et~al.}{1963}]{b20} Prem, G. W., Christ, W., Smap, J.,
-Wills, J. A. (1963). {\it Topics in Stochastic Processes.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{Rahul}{1981}]{b1} Rahul, S. R. (1981).
-Industrial ecology: A  critical review. {\it International Journal of
-Environment and Pollution} {\bf 6,} 371--375.
-
-\bibitem[\protect\citeauthoryear{Ram  and Shyam}{1972}]{b6} Ram, R. D.
-and Shyam, S. (1972). {\it Topics in Stochastic Process.} New York: Academic  Press.
-
-\bibitem[\protect\citeauthoryear{Ravan  and Hari}{1983a}]{b21} Ravan,
-M. and Hari, S. (1983). Industrial ecology: A  critical review.
-{\it International Journal of Environment and Pollution} {\bf 6,} 389--395.
-
-\bibitem[\protect\citeauthoryear{Ravan  and Hari}{1983b}]{b22}
-Ravan, M. and Hari, S. (1984). Industrial ecology: A  critical
-review. {\it International Journal of Environment and Pollution} {\bf 7,} 512--519.
-
-\bibitem[\protect\citeauthoryear{Sharma et~al.}{1984}]{b16} Sharma,
-F. J. (1984). {\it Topics in Stochastic Process.} New York: Academic Press.
-
-\bibitem[\protect\citeauthoryear{Vim   and Potter}{1988}]{b23} Vim, W.
-E. and Potter, H. J. (1988). A  critical
-review. {\it International Journal of Environment and Pollution} {\bf 9,} 635--641.
-
-\end{thebibliography}
-
-\label{lastpage}
+%% \begin{table*}
+%% \caption{Repeat length of longer allele by age of onset class}
+%% \begin{tabular}{ccc}
+%% table text
+%% \end{tabular}
+%% \end{table*}
 

### 2012-08-07 paper/paper.tex
Copied material on the immigration death process from the documents in docs to the appendix.

@@
 
-\author{B. Calderhead\affil{1}{UCL}, C. S. Gillespie\affil{2}{NCL}}
+\author{Ben Calderhead\affil{1}{University College London, London, United Kingdom}, Colin S. Gillespie\affil{2}{Newcastle University, Newcastle upon Tyne, United Kingom}}
 % \email{b.calderhead@ucl.ac.uk}
@@
 %% When adding keywords, separate each term with a straight line: |
-\keywords{term | term | term}
+\keywords{moment closure | stochastic | inference}
 
@@
 %% or, for appendix with title, use square brackets:
-%% \appendix[Appendix Title]
+
+%Taken from the tex file in the docs folder
+%Not edited yet
+\appendix[Immigration-death process]
+
+This model has a single species, $N(t)$.
+The first reaction represents a constant immigration rate, and occurs with rate $k_1$.
+The second reaction represents death in the $N$ population and occurs with rate $k_2 N(t)$.
+The model can be represented by the coupled (pseudo) reactions,
+\begin{equation}\label{1}
+R_1: \emptyset  \xrightarrow{\phantom{a}k_1\phantom{a}} N 
+\quad \text{and} \quad
+R_2: N  \xrightarrow{\phantom{a}k_2\phantom{a}} \emptyset.
+\end{equation}
+The forward Kolmogorov equation (or CME) for this model is
+\[
+dp_{n}(t)/dt = k_1 p_{n-1}(t) +  k_2 (n+1) p_{n+1}(t) 
+- (k_1 + k_2 n) p_{n}(t) \;.
+\]
+This equation can be solved exactly using a generating function approach.
+
+\subsection{Moments}
+
+The general idea of \textit{moment closure} is to represent the analytically intractable moments of the process as a set of ODEs.
+The solutions of these ODEs provide approximations for the moments.
+With this particular system, we can solve the ODEs analytically - so the moments are exact.
+
+The marginal means of the process are:
+\[
+E[n(t) | n(0) = n_0 ] = \frac{k_1}{k_2}(1-e^{-k_2 t}) + n_0 e^{-k_2 t} \;.
+\]
+Notice that as $t \rightarrow \infty$,
+\[
+E[n(t) | n(0) = n_0 ] = \frac{k_1}{k_2} \;.
+\]
+The marginal variance is
+\[
+Var[n(t) | n_0]  = \left(\frac{k_1}{k_2} + n_0e^{-k_2 t}\right)(1-e^{-k_2 t}) \;.
+\]
 

### 2012-08-07 paper/paper.tex
Added appendix on the aphid model

@@
 
+%Just copied from the RSS paper
+\appendix[Aphid model]
+
+Following \cite{Matis06}, we assume a linear aphid population birth rate of $\lambda N(t)$ where $N(t)$ denotes the size of the aphid population at time $t$.
+As discussed in \cite{Prajneshu98}, aphids excrete honey-dew, forming a cover on the leaf surface and causing aphid starvation.
+As the area covered by excretion at time $t$ is proportional to the cumulative population size at time $t$, $C(t)$, we assume a death rate of $\mu N(t)C(t)$ and for simplicity, assume that there is no removal or decomposition of honey-dew \cite{Matis06,Matis07a,Matis08}.
+The model can be represented by the coupled (pseudo) reactions,
+\begin{align}
+N & \xrightarrow{\phantom{a}\lambda\phantom{a}} 2N + C \label{2.1} \\
+N+C & \xrightarrow{\phantom{a}\mu\phantom{a}} C \label{2.2}
+\end{align}
+since clearly, an occurrence of (\ref{2.1}) will lead to a unit increase in both $N$ and $C$ whereas the reaction in  (\ref{2.2}) will give a unit decrease in $N$ but leave $C$ unchanged.
+Such models are known in the literature as stochastic kinetic models; see \cite{Wilkinson06} for a concise introduction.
+We can express the probabilistic laws governing the time evolution of the process by considering a small interval $(t,t+dt]$, namely
+\begin{align}
+\Pr\left\{N(t+dt)=n(t)+1,\,C(t+dt)=c(t)+1\,|\,n(t),c(t)\right\}&=\lambda n(t)dt+o(dt) \label{2.3} \\
+\Pr\left\{N(t+dt)=n(t)-1,\,C(t+dt)=c(t)\,|\,n(t),c(t)\right\}&=\mu n(t)c(t)dt+o(dt),\label{2.4}
+\end{align}
+and we adopt the convention that upper case denotes random variable and lower case denotes the realisation.
+The expressions in (\ref{2.3}) and (\ref{2.4}) describe a Markov jump process where each event occurs at a particular rate dependent on the current state of the system.
+Note that ignoring stochasticity leads to a deterministic model where the time course behaviour of $N(t)$ and $C(t)$ is described by the set of differential equations,
+\[
+\left\{\begin{array}{l}
+\displaystyle\frac{dN(t)}{dt}=\lambda N(t)-\mu N(t)C(t)\\
+\\
+\displaystyle\frac{dC(t)}{dt}= \lambda N(t)
+\end{array}\right.
+\]
+
 \begin{acknowledgments}

### 2012-09-24 graphics/figure1.R
Stochastic simulation of the immigration death process

@@ -1,0 +1,16 @@
+library(ggplot2)
+require(reshape2)
+require(grid)
+theme_set(theme_bw(base_size = 10))
+
+dd_dis = read.csv("data/immigration_death.csv", header=TRUE)
+dd_full = read.csv("data/full_immigration_death.csv", header=TRUE)
+
+g = ggplot(dd_full, aes(times, n)) + 
+    geom_step() + 
+    geom_point(data=dd_dis, aes(times, n), size=3, colour="red") + 
+    xlab("Time") + ylab("Population")
+
+pdf("graphics/figure1.pdf", width=3, height=3)
+print(g)
+dev.off()

### 2012-09-24 Immigration-death/mcmc.R
Added code for creating the expected fisher information.

@@ -29,4 +29,6 @@ k1 = seq(log10(1.1),log10(100),  length.out=500)
 k2 = seq(log10(1.1),log10(100), length.out=500)
 d = outer(k1, k2, function(k1, k2) log_likelihood(k1, k2, dd[,1], dd[,2]))
 image(log10(k1), log10(k2), exp(d))
+
+
 points(1, 1,pch=18)

### 2012-09-24 Immigration-death/tensor_calculation.R

@@ -1,37 +1,39 @@
 ##Moments
 ##k1 = immigration rate, k2 =death
-E = function(k1, k2, n0, t) {
-    (k1-k1*exp(-k2*t)+n0*exp(-k2*t)*k2)/k2
+E = function(k1, k2, n0, tau) {
+    (k1-k1*exp(-k2*tau)+n0*exp(-k2*tau)*k2)/k2
 }
 
-V = function(k1, k2, n0, t) {
-    (-n0*exp(-2*k2*t)*k2+k1-k1*exp(-k2*t)+n0*exp(-k2*t)*k2)/k2
+V = function(k1, k2, n0, tau) {
+    (-n0*exp(-2*k2*tau)*k2+k1-k1*exp(-k2*tau)+n0*exp(-k2*tau)*k2)/k2
 }
 
 ##First-order 
-dE_dk1 = function(k1, k2,n0, t) {
-    (1-exp(-k2*t))/k2    
+dE_dk1 = function(k1, k2,n0, tau) {
+    (1-exp(-k2*tau))/k2    
 }
 
-dE_dk2 = function(k1, k2,n0, t) {
-    -k1*(1-exp(-k2*t))/k2^2+k1*t*exp(-k2*t)/k2-n0*t*exp(-k2*t)   
+dE_dk2 = function(k1, k2, n0, tau) {
+    -k1*(1-exp(-k2*tau))/k2^2+k1*tau*exp(-k2*tau)/k2-n0*tau*exp(-k2*tau)   
 }
 
 ##Derivative of Variance wrt to theta
-dV_dk1 = function(k1, k2,n0, t) {
-    (1-exp(-k2*t))/k2
+dV_dk1 = function(k1, k2,n0, tau) {
+    (1-exp(-k2*tau))/k2
 }
-dV_dk2 = function(k1, k2,n0, t) {
-    (2*n0*t*exp(-2*k2*t)*k2-n0*exp(-2*k2*t)+k1*t*exp(-k2*t)-n0*t*exp(-k2*t)*k2+n0*exp(-k2*t))/k2-(-n0*exp(-2*k2*t)*k2+k1-k1*exp(-k2*t)+n0*exp(-k2*t)*k2)/k2^2
+dV_dk2 = function(k1, k2,n0, tau) {
+    (2*n0*tau*exp(-2*k2*tau)*k2-n0*exp(-2*k2*tau)+k1*tau*exp(-k2*tau)-
[…]

### 2012-09-24 graphics/manifold.R

@@ -1,23 +1,80 @@
-dd = NULL
-k1 = seq(0.5, 1.5, 0.01/3)
-files = list.files(pattern="^[0-9]{1,3}.csv$")
-
-for(i in seq_along(files)) {
-  dd_tmp = read.delim(files[i], header=FALSE)[1:616,]
-
-  dd = rbind(dd, dd_tmp)
-}
-dd$k2 = seq(0.07, 1.3, 0.006/3)
-i = as.numeric(sub(".csv", "", files))
-
-dd$k1 = rep(k1[i], each=616)
-write.csv(dd, file="exact_fisher.csv", row.names=FALSE)
-
-#1.5-1 by 0.01/3
-#0.07-1.3 by 0.006/3
-
-?heatmap
 require(ggplot2)
+require(reshape2)
+require(grid)
+theme_set(theme_bw(base_size = 11))
+vplayout = function(x, y) 
+    viewport(layout.pos.row = x, layout.pos.col = y)
+
+std = function(value) {
+    value/max(value)
+}
+
+dd_e = read.csv("data/exact_fisher.csv", header=TRUE)
+dd_e$type = "Exact"
+colnames(dd_e)[1:3] = c("d.dk1k1", "d.dk1k2", "d.dk2k2")
+
+dd_mc = read.csv("data/mc_fisher.csv", header=TRUE)
+dd_mc$type = "Moment~Closure"
+
+# 
+# dd_mc[3] = std(dd_mc[3])
+# dd_mc[4] = std(dd_mc[4])
+# dd_mc[5] = std(dd_mc[5])
+# dd_e[1] = std(dd_e[1])
+# dd_e[2] = std(dd_e[2])
+# dd_e[3] = std(dd_e[3])
+# apply(dd_e[1:3], 2, range)
+# apply(dd_mc[3:5], 2, range)
+
+dd = rbind(dd_mc, dd_e)
+dd=dd[dd$k1 > 1.2 & dd$k2 > 1, ]
+dd$close11 = "d^2/dk[1] * dk[1]"
+dd$close12 = "d^2/dk[1] * dk[2]"
+dd$close22 = "d^2/dk[2] * dk[2]"
+
+# 
+# dd = melt(dd, c("k1", "k2", "type"))
 head(dd)
 
-ggplot(dd) + geom_raster(aes(x=k1, y=k2, fill=V3))
+g = ggplot(dd,aes(k1, k2)) + 
[…]

### 2012-09-24 paper/paper.tex
Added bibtex file
Added figures to paper.

@@
 \documentclass{pnastwo}
-
+\bibliographystyle{pnas}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\usepackage[dvips]{graphicx}
+\usepackage{graphicx}
 
@@
 % Sample bibliography item in PNAS format:
-%% \bibitem{in-text reference} comma-separated author names up to 5,
-%% for more than 5 authors use first author last name et al. (year published)
-%% article title  {\it Journal Name} volume #: start page-end page.
-%% ie,
+
+\bibliography{refs}    
+%% Enter the largest bibliography number in the facing curly brackets
+%% following \begin{thebibliography}
+
+%  \begin{thebibliography}{}
+% % \bibitem{in-text reference} comma-separated author names up to 5,
+% % for more than 5 authors use first author last name et al. (year published)
+% % article title  {\it Journal Name} volume #: start page-end page.
+% % ie,
 % \bibitem{Neuhaus} Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) 
@@
 % {\it Proc Natl Acad Sci USA} 88:10362-10366.
-
-%% Enter the largest bibliography number in the facing curly brackets
-%% following \begin{thebibliography}
-
-% \begin{thebibliography}{}
 %  
@@
 
+\begin{figure}[ht]
+\begin{center}
+\centerline{\includegraphics[]{../graphics/figure1}}
+\end{center}
+\caption{Stochastic simulation of the immigration-death process, with parameters
+$k_1=k_2=1$ and $n(0)=0$. The black line shows the full stochastic realisation, 
+the red dots indiciate the observed data.}
+\end{figure}
+\begin{figure*}[ht]
+\begin{center}
+\centerline{\includegraphics[width=.7\textwidth]{../graphics/figure2}}
+\caption{Comparison of the exact and the moment closure expected fisher information matrix. \textit{Note: I'm not happy with the layout, still working on that}.}\label{afoto2}
+\end{center}
+\end{figure*}
+% 
+% \begin{figure*}
+% \centering
+% \includegraphics[]{../graphics/figure1}
+% \caption{blah}
+% \end{figure*}
+
 \end{document}

### 2012-09-25 graphics/manifold.R
Updated ID expected fisher information contour plot.

@@ -1,6 +1,7 @@
 require(ggplot2)
 require(reshape2)
 require(grid)
+library(gridExtra)
 theme_set(theme_bw(base_size = 11))
 vplayout = function(x, y) 
     viewport(layout.pos.row = x, layout.pos.col = y)
@@ -32,33 +33,62 @@ dd$close11 = "d^2/dk[1] * dk[1]"
 dd$close12 = "d^2/dk[1] * dk[2]"
 dd$close22 = "d^2/dk[2] * dk[2]"
 
+
+dd = expand.grid(x=1:10, y=1:10)
+dd = data.frame(dd, type=rep(LETTERS[1:2], each=100), 
+                var =rep(c("C", "D"), each=200) )
+dd$z = rnorm(400, rep(c(0, 100), each=200))
+
+
+p1 <- ggplot(subset(dd, var=="C"), aes(x,y))+
+    geom_raster(aes(fill=z)) + facet_grid(type ~ var) + 
+    theme(legend.position="bottom", plot.margin = unit(c(1,-1,1,0.2), "line"))
+p2 <- ggplot(subset(dd, var=="D"), aes(x,y))+
+    geom_raster(aes(fill=z)) + facet_grid(type ~ var) + 
+    theme(legend.position="bottom", 
+          plot.margin = unit(c(1,1,1,-0.8), "line"),
+          axis.text.y = element_blank(), axis.ticks.y = element_blank()) + ylab(NULL)
+grid.arrange(arrangeGrob(p1, p2, nrow = 1))
+
 # 
 # dd = melt(dd, c("k1", "k2", "type"))
 head(dd)
 
 g = ggplot(dd,aes(k1, k2)) + 
-    scale_x_continuous(expand=c(0, 0)) + 
+    scale_x_continuous(expand=c(0, 0.01)) + 
     scale_y_continuous(expand=c(0, 0)) + 
     xlab(expression(k[1])) + 
     theme(legend.position="bottom") + 
-    scale_fill_continuous(name = "") + 
-     theme(plot.margin = unit(c(0,0,0,0), "cm"))
+    scale_fill_continuous(name = "") 
+     
 
-g1 = g + geom_raster(aes(x=k1, y=k2, fill=d.dk1k1))  + 
+g1 =g + geom_raster(aes(x=k1, y=k2, fill=d.dk1k1))  + 
     stat_contour(aes(z=d.dk1k1)) +
     facet_grid(type~close11, labeller= label_parsed) 
+
[…]

### 2012-10-22 ManifoldMomentClosure.tex
Testing SourceTree software for mac...

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{algorithm,algorithmic}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Manifold Sampling for Moment Closure}
\author{BC}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

\section{Expected Fisher Information for Moment Closure}

We start by considering the likelihood induced by the moment closure approach using a Gaussian approximation.  Following from Equation 7 in the Stats and Computing paper, the pseudo-likelihood follows as

\begin{eqnarray}
\hat{L}( \boldsymbol\theta | {\bf Z} ) &=& \prod_{i=1}^{T-1} \hat{p}( {\bf Z}(t_{i+1}) | {\bf Z}(t_i) ) \notag \\
&=& \prod_{i=1}^{T-1} {N}_{ {\bf Z}(t_{i+1}) } \left( \varphi_i, \boldsymbol\Sigma_{i} \right)
\end{eqnarray}

\noindent where

\begin{eqnarray}
\varphi_i &=& \hat{\text{E}}( {\bf Z}(t_{i+1}) | {\bf Z}(t_i) ) \\
\boldsymbol\Sigma_i &=& \hat{\text{Var}} ( {\bf Z}(t_{i+1}) | {\bf Z}(t_i) )
\end{eqnarray}

\noindent such that $\varphi_i$ and $\boldsymbol\Sigma_i$ are the mean and covariance, respectively, under the moment closure approximation.  We now need to calculate the metric tensor for this pseudo-likelihood, which is given by the Expected Fisher Information.  Using the Gaussian approximation above, the Expected Fisher Information is easy to calculate and takes a standard form; due to the Markov property it turns out to be the sum of Expected Fisher Informations for each ${\bf Z}_{t_i}$.  For ease of notation, let us denote $\hat{L}_i = \hat{p}( {\bf Z}(t_{i+1}) | {\bf Z}(t_i) )$.  The overall Expected Fisher Information follows as

\begin{eqnarray}
\text{FI}_{\hat{L}} &=& \text{E}_{\hat{L}} \left( \frac{\partial \log \hat{L}}{\partial\boldsymbol\theta}^T \frac{\partial \log \hat{L}}{\partial\boldsymbol\theta} \right) \notag\\
&=& \sum_{i=1}^{T-1} \text{E}_{\hat{L}_i} \left( \frac{\partial \log \hat{L}_i}{\partial\boldsymbol\theta}^T \frac{\partial \log \hat{L}_i}{\partial\boldsymbol\theta} \right)\\
&=& \sum_{i=1}^{T-1} \text{FI}_{\hat{L}_i}
\end{eqnarray}

\noindent The $\hat{L}_i$s are all Gaussian, and so the standard expressions for the Expected Fisher Information of multivariate Gaussians may be used for each component of the sum.  In particular, the $(m,n)$th component of the $i$th FI is given by

\begin{eqnarray}
\text{FI}_{\hat{L}_i (m,n)} = \frac{\partial \varphi_i}{\partial \theta_m}^T \boldsymbol\Sigma_i^{-1} \frac{\partial \varphi_i}{\partial \theta_n} + \frac{1}{2}\text{tr}\left( \boldsymbol\Sigma_i^{-1} \frac{\partial \boldsymbol\Sigma_i}{\partial \theta_m} \boldsymbol\Sigma_i^{-1} \frac{\partial \boldsymbol\Sigma_i}{\partial \theta_n} \right)
\end{eqnarray}

\section{Simplified mMALA Sampler}

We may construct a simple Metropolis-Hastings proposal mechanism that makes use of the local geometry around each point in the parameter space.  We note that we are working with the log-likelihood and its associated geometry here.  In particular, our proposal will have a mean based on the current parameters plus a small move in the direction of the natural gradient, and a covariance equal to the scaled inverse of the Expected Fisher Information at the current point.

The natural gradient is defined as the inverse of the Expected Fisher Information (the metric tensor) multiplied by the standard gradient of the log-likelihood.  The mean of the proposal at $\boldsymbol\theta$ is therefore given by,

\begin{eqnarray}
\boldsymbol\mu(\boldsymbol\theta) = \boldsymbol\theta + \frac{\epsilon^2}{2} \text{FI}_{\hat{L}}^{-1}(\boldsymbol\theta)  \frac{\partial \hat{L}(\boldsymbol\theta)}{\partial \boldsymbol\theta}
\end{eqnarray}

\noindent and the covariance of the proposal is given by,

\begin{eqnarray}
\boldsymbol\Sigma(\boldsymbol\theta) = \epsilon^2 \text{FI}_{\hat{L}}^{-1}(\boldsymbol\theta)
\end{eqnarray}

The metric tensor, in this case given by the Expected Fisher Information, is usually represented by $G$, and the log-likelihood by $L$.  Using this notation, the general simplified mMALA algorithm is given in full in Algorithm 1.

\begin{algorithm}[h]                      % enter the algorithm environment
\caption{Simplified Manifold MALA}          % give the algorithm a caption
\label{alg:SmMALARecipe}                           % and a label for \ref{} commands later in the document
\begin{algorithmic}[1]                   % enter the algorithmic environment
\STATE Initialise current $\boldsymbol\theta$
\FOR{IterationNum $= 1$ to NumSamples}
\STATE Sample $\boldsymbol\theta^{\textsf{new}} \sim p(\boldsymbol\theta^{\textsf{new}}|\boldsymbol\theta) = N(\mu(\boldsymbol\theta, \epsilon), \Sigma(\boldsymbol\theta, \epsilon))$, \\where $\mu(\boldsymbol\theta, \epsilon) = \boldsymbol\theta + \frac{\epsilon^2}{2} {G}^{-1}(\boldsymbol\theta) \nabla_{\boldsymbol\theta} {L}(\boldsymbol\theta)$ and $\Sigma(\boldsymbol\theta, \epsilon) = \epsilon^2 G^{-1}(\boldsymbol\theta)$
\STATE Calculate current log-likelihood ${L}(\boldsymbol\theta)$ and proposed log-likelihood ${L}(\boldsymbol\theta^{\textsf{new}})$
\STATE Calculate $\log(p(\boldsymbol\theta^{\textsf{new}}|\boldsymbol\theta))$, $\log(p(\boldsymbol\theta|\boldsymbol\theta^{\textsf{new}}))$, $\log($Prior$(\boldsymbol\theta))$, $\log($Prior$(\boldsymbol\theta^{\textsf{new}}))$
\STATE LogRatio $= {L}(\boldsymbol\theta^{\textsf{new}}) + \log($Prior$(\boldsymbol\theta^{\textsf{new}})) + \log(p(\boldsymbol\theta|\boldsymbol\theta^{\textsf{new}})) - {L}(\boldsymbol\theta) - \log($Prior$(\boldsymbol\theta)) - \log(p(\boldsymbol\theta^{\textsf{new}}|\boldsymbol\theta))$
\IF{LogRatio $> 0$ \OR LogRatio $> \log$(rand)}
\STATE Set $\boldsymbol\theta = \boldsymbol\theta^{\textsf{new}}$
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

\end{document}

### 2013-12-16 paper/paper.tex
Merging introduction to paper

@@
 
-\author{Ben Calderhead\affil{1}{University College London, London, United Kingdom}, Colin S. Gillespie\affil{2}{Newcastle University, Newcastle upon Tyne, United Kingom}}
+\author{Ben Calderhead\affil{1}{University College London, London, United
+    Kingdom}, Colin S. Gillespie\affil{2}{Newcastle University, Newcastle upon
+    Tyne, United Kingdom}}
 % \email{b.calderhead@ucl.ac.uk}
@@
 
-\begin{abstract} -- enter abstract text here -- \end{abstract}
+\begin{abstract}
+We introduce an efficient and novel approach for Bayesian statistical
+inference of stochastic population models with complex dynamics,
+unobserved species and large numbers of parameters. Despite their
+increasing ubiquity, Bayesian analysis of such stochastic models still
+presents major challenges, as the exact likelihood is often computa-
+tionally intractable for realistically sized models and full exploration
+of the parameter space may be inhibited by very strong correla-
+tion structure. Our methodology exploits the natural underlying ap-
+proximate Riemannian geometry of the model parameters induced
+by estimating the likelihood using moment closure techniques. We
+demonstrate how this geometric approach allows us to perform in-
+ference in a statistically and computationally efficient manner, and
+in doing so we highlight the link between the Riemannian structure
+of the parameters and sensitivity analysis of the dynamical system.
+We illustrate the performance of our approach using synthetic ex-
+amples, as well as a realistically-sized partially observed ecological
+model with 50 unknown parameters, with data describing the evolu-
+tion of aphid populations. For the examples in this paper, efficient
+computer code written in Matlab and C is available from the authors
+upon request.
+\end{abstract}
 
@@
 
+The use of stochastic models is rapidly becoming ubiquitous in many areas of the
+natural sciences, where it is necessary to model the intrinsic stochasticity of
+a dynamical system in or- der to fully characterise its main modes of behaviour
+[REFs]. Markov Jump Process models - what are they and why are they useful?
+
+Mathematical approaches are essential for making sense of these complex models;
+well developed for deterministic mod- els, such as ordinary differential
+equations, but still underde- veloped for stochastic models.
+
+Why? Likelihood is often computationally intractable for
+all but the simplest of Markov Jump Process models.
+Sensitivity analysis plays an important role in elucidating
+the behaviour of mathematical models with complex dynam
+ics - how do variations in parameters accpet the output? Only
+fairly recently have methods been published for estimating the
+local sensitivity information for a stochastic chemical kinetic
+model via use of the linear noise approximation [REFs].
+local versus global sensitivity analysis
+
+Sensitivity information at the maximum likelihood is
+based on a linearisation around this point and is thus a lo-
+cal measure. Given the strong nonlinearities present in many
+current models, this provides limited information about the
+dynamics of the system.
+
+FIM is often used to describe the local sensitivity at the
+maximum likelihood however this makes strong assumption
+of normality around that set of parameters, which may be
+inappropriate for strongly nonlinear systems.
+
+Bayesian methodology in particular offers a consistent,
+probabilistic framework for reasoning under uncertainty,
+which may occur both in the data and the model structure
+itself.
+
+Posterior distribution as a global measure of sensitivity of
+the system. However drawing samples from this is generally
+very challenging.
+
+FIM provides a link between local and global sensitivity
+analysis.
+
+FIM is usually used to measure the reliability of inferences
+around the maximum likelihood and is often understood ge-
+ometrically as the curvature of the log-likelihood around this
+point. However, the expected Fisher Information in fact gives
+us much more geometric information than this; it defines a
+metric tensor at any point of parameter space and thus pro-
+vides a natural representation of the parameter space as a
+Riemannian manifold, where distances between two sets of
+parameters are defined in terms of the relative changes they
+induce on the likelihood.
+
+We use a moment closure technique to obtain local ap-
+proximations to the likelihood at the current point - such an
+approach extends the LNR as we may now choose the pdf
+with which to approximate the local likelihood. We demon-
+strate how the expected Fisher Information may be obtained
+from this moment closure approximation and that this forms
+a Riemannian manifold that approximates the local sensitiv-
+ity of the model at each possible set of parameters. Further,
+we demonstrate the utility of this using differential geometric
+MCMC algorithms that allow us to sample from the poste-
+rior distribution of the parameters of stochastic population
+models, by utilising the local sensitivity information at each
+point. Essentially a locally adaptive algorithm that exploits
+the local sensitivity at each point, allowing us to move from
+local to global sensitivity information in a computationally
+and statistically efficient manner.
+
 \section{Introduction}
@@
 \end{itemize}
+Why MC is better than LNA
+\begin{itemize}
+\item Higher-order approximation - REF: J CHEM Phy
+\item Use other closure distributions: Lognormal - beta-bionomial
+\item REF other recent MC PNAS papers - Kazinesis and Zurich paper
+\end{itemize}
 
@@
 For example in ecology, where we often have to deal with discrete noisy data.
-Importance of parametric sensitivity has already been shown for determining vital properties of biological systems such as robustness and also in experimental design where the sensitivity gives information about the identifiability of individual rate constants.
+Importance of parametric sensitivity has already been shown for determining vital properties of biological systems such as robustness and also in experimental design where the sensitivity gives information about the identifiably of individual rate constants.
 
@@
   \item Calculate exact proposal for comparison (\textbf{17/8: CSG})
-  \item Construct LNA model for ID (\textbf{14/9: CSG/BC})
   \item Graphs:
     \begin{itemize}
-    \item Data: \textbf{17/8: CSG}
-    \item Geometry proposal: 3 proposals for the 3 derviates: k1\^2, k1k2, k2\^2
-      \textbf{24/8: }
-    \item Likelihood: Exact likelihood vs LNA vs MC \textbf{24/8: }
-    \item Delay acceptance(?)
-    \item Sampling efficiences M-H vs RM (appendix)
+    \item Data:
+    \item Geometry proposal: 2 proposals for the 3 derivatives: k1\^2, k1k2, k2\^2
+    \item Likelihood: Exact likelihood vs MC
+    \item Sampling efficiencies M-H vs RM (appendix)
     \end{itemize}
@@
     \begin{itemize}
-    \item Construct moment equations (\textbf{17/8: CSG}) Lognormal?
+    \item Construct moment equations:  Lognormal or Beta Binomial
     \item Construct proposal
-    \item Delay acceptance
     \item Run experiments
@@
       \item Data
-      \item Sampling efficiences M-H vs RM (appendix)
-      \item Posterior compare to Stumpf
+      \item Sampling efficiencies M-H vs RM (appendix)
       \end{itemize}
@@
 36 parameters - 18 birth, 18 death. 3 water treatments, 3 nitrogen treatments
-and 3 blocks, with interactions. 5*27 (I think) latent data sets. Exploit Sub-mannifolds for choosing parameter sets
+and 3 blocks, with interactions. 5*27 (I think) latent data sets. Exploit Sub-manifolds for choosing parameter sets
 Poisson error structure.
@@
     \item Construct proposal (appendix)
-    \item Delay acceptance
     \item Run experiments
@@
       \item Data \textbf{Done}
-      \item Sampling efficiences M-H vs RM; ESS
+      \item Sampling efficiencies M-H vs RM; ESS
       \item Posteriors
@@
 \item Use of geometry vital in tackling real problems
-\item Could also use other approximation schemes such as the LNA??
 \end{itemize}
-
 %% == end of paper:
@@
 $k_1=k_2=1$ and $n(0)=0$. The black line shows the full stochastic realisation, 
-the red dots indiciate the observed data.}
+the red dots indicate the observed data.}\label{F1}
 \end{figure}
@@
 \centerline{\includegraphics[width=.7\textwidth]{../graphics/figure2}}
-\caption{Comparison of the exact and the moment closure expected fisher information matrix. \textit{Note: I'm not happy with the layout, still working on that}.}\label{afoto2}
+\caption{Comparison of the exact and the moment closure expected fisher information matrix. }
+\label{F2}
 \end{center}

### 2013-12-16 Simulation/graphics.R
Adding graphics file

@@ -1,0 +1,37 @@
+library(ggplot2)
+library("scales")
+##Time course data
+head(dd)
+dd = read.csv("data/immigration_death_k1_1_k2_1.csv")
+full = read.csv("data/immigration_death_full_k1_1_k2_1.csv")
+g1 = ggplot(full, aes(x=times, y=n)) + 
+    geom_step() + 
+    xlab("Time") + ylab("Population")
+
+pdf("figure1.pdf", width=4, height=2.5)
+print(g1)
+sink=dev.off()
+system("pdfcrop figure1.pdf")
+
+pdf("figure1b.pdf", width=4, height=2.5)
+print(g1 +geom_point(data=dd, col=2, size=3))
+sink=dev.off()
+system("pdfcrop figure1b.pdf")
+
+###likelihood for ID process
+g = ggplot(df, aes(fill=exp(z), x=x, y=y)) + 
+    geom_raster() + 
+    guides(fill=FALSE) + 
+    xlab(expression(k[1])) + ylab(expression(k[2])) +
+    scale_fill_continuous(low="white", high="red") + 
+    xlim(c(0,10)) + ylim(c(0,10))
+g = g + scale_y_continuous(expand=c(0, 0)) + 
+    scale_x_continuous(expand=c(0, 0))
+g = g + stat_contour(aes(z=exp(z)), size=0.2)
+pdf("figure2.pdf", width=4, height=2.5)
+print(g)
+sink=dev.off()
+system("pdfcrop figure2.pdf")
+
+
+
